---
title: "Code Checking"
output: html_notebook
---

# Results presentation

```{r}
df <- readRDS("data/mean_travel_time_ranking_2011.rds")
mean <- 23.8
sd <- 3.6 #2 #3.6 #c(2, 3.6, 6)
K <- c(10)#(51, 40, 30, 20, 10, 5)
corr <- c(0.5)#,0.5,0.9)
alpha <- c(0.05)#c(0.05, 0.1, 0.15, 0.2)
B <- 600

set.seed(123974)
true_theta <- rnorm(K, mean, sd)
true_sds <- df$S[1:K]
    
true_theta
```

# Block Diagonal Correlation

## Function to create block corr

```{r}
block_corr <- function(block_sizes, rho_within, rho_between) {
  B <- length(block_sizes)
  N <- sum(block_sizes)

  if (length(rho_within) == 1) {
    rho_within <- rep(rho_within, B)
  }

  Sigma <- matrix(rho_between, nrow = N, ncol = N)
  diag(Sigma) <- 1

  idx <- 1
  for (b in seq_len(B)) {
    block_idx <- idx:(idx + block_sizes[b] - 1)
    Sigma[block_idx, block_idx] <- rho_within[b]
    diag(Sigma[block_idx, block_idx]) <- 1
    idx <- idx + block_sizes[b]
  }

  return(Sigma)
}

block1 <- block_corr(block_sizes=c(4,6), rho_within=c(0.85, 0.25), rho_between=0.0)
K <- c(dim(df)[1])
# none, mkbyn,kibam, marcos, d
block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0, 0.8, 0.8, 0.8, 0.8, 0.8), rho_between=0.0) #%>% View()
```

List of block corrs used:
 - `block_corr(block_sizes=c(K/2,K/2), rho_within=c(0.9, 0.1), rho_between=0.0)`
 - `block_corr(block_sizes=c(.3*K,.7*K), rho_within=c(0.9, 0.1), rho_between=0.0)`
 - `block_corr(block_sizes=c(.2*K,.3*K, .5*K), rho_within=c(0.9, 0.5, 0.1), rho_between=0.0)`
 - `block_corr(block_sizes=c(.2*K,.3*K, .5*K), rho_within=c(0.1, 0.5, 0.9), rho_between=0.0)`
 
## Checking Positive Definiteness

```{r}
# K <- 50
# 
# for (K in c(10,20,30,40,50)) {
#   block_unb <- block_corr(block_sizes=c(.2*K,.3*K, .5*K), rho_within=c(0.1, 0.5, 0.9), rho_between=0.0)
#   tol = 1e-8
#   eval <- eigen(block_unb)$values
#   print(paste("PD for K=",K, ":", all(eval > -abs(tol * max(eval)))))
# }

# K=64
# block_unb <- block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0, 0.8, 0.8, 0.8, 0.8, 0.8), rho_between=0.0)
# K=18
# corr_matrix <-block_corr(block_sizes=c(2, 2, 8, 6), rho_within=c(0, 0.9, 0.9, 0.9), rho_between=0.0)

K=64
block_unb <- block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0.0, 0.9, 0.9, 0.9, 0.9, 0.9), rho_between=0.0)  #block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0.0, 0.3, 0.3, 0.3, 0.3, 0.3), rho_between=0.0) #block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0.0, 0.1, 0.1, 0.1, 0.1, 0.1), rho_between=0.0) 


corr_matrix <-block_corr(block_sizes=c(2, 12, 10, 2, 11, 27), rho_within=c(0.9, 0.9, 0.9, 0.9, 0.9, 0.1), rho_between=0.0) 


generate_corr_mat <- function(r){
  block_corr(block_sizes=c(2, 12, 10, 2, 11, 27), rho_within=rep(r, 6), rho_between=0.0)
}


for (corr_matrix in lapply(c(0.0, 0.1, 0.3, 0.5, 0.7, 0.9), generate_corr_mat)){
  eval <- eigen(corr_matrix)$values
  tol = 1e-8
  print(paste("PD for K=",K, ":", all(eval > -abs(tol * max(eval)))))
}

```

```{r}
selected_columns <- c('independent', 'bonferroni', 'nonrankbased')
test <- c('low', 'med', "high")

unlist(lapply(test, function(x) {paste(selected_columns, x, sep = '_')}))
```




# Real Data Application


```{r}
source("R/generate_true_theta.R")

cand <- generate_true_theta_rd(persist_df = FALSE)

cand$Makabayan <- ifelse(cand$Party == 'MKBYN', 1, 0)
```


```{r}
cand
```



```{r}
# cand %>% 
#   mutate(Voting_for_dec = `Voting For`/100) %>%
#   mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
#   select(-Voting_for_dec) %>% arrange(desc(`Voting For`)) %>% View()
```


```{r}
# cand %>% 
#   mutate(Voting_for_dec = `Voting For`/100) %>%
#   mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
#   select(-Voting_for_dec) %>% arrange(desc(`Voting For`)) %>%  arrange(DuterTen, Alyansa, KiBam, Makabayan) 
```

```{r}
K <- c(dim(df)[1])
# none, mkbyn,kibam, marcos, d
# block_corr(block_sizes=c(2, 2, 8, 6), rho_within=c(0, 0.8, 0.8, 0.8, 0.8), rho_between=0.0)
# block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0, 0.8, 0.8, 0.8, 0.8, 0.8), rho_between=0.0) #%>% View()
```




```{r}
# process_ci_result <- function(result, K) {
#   tuple_list <- t(apply(
#     data.frame(
#       ci_lower = result$ci_lower,
#       ci_upper = result$ci_upper
#     ), 
#     1, 
#     function(row) as.numeric(row)
#   ))
#   
#   rank_range_length <- sapply(1:K, function(x) 
#     length(get_ranks(x, tuple_list)$ranks)
#   )
#   list(
#     t1 = get_t1(rank_range_length),
#     t2 = get_t2(rank_range_length),
#     t3 = get_t3(rank_range_length)
#   )
# }
``` 








```{r}
block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0.0, 0.1, 0.1, 0.1, 0.1, 0.1), rho_between=0.0) %>% View()
```



```{r}
source("R/simulate/compute_ci.R")
source("R/simulate/compute_metrics.R")

# df <- cand %>%
#   mutate(Voting_for_dec = `Voting For`/100) %>%
#   mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
#   select(-Voting_for_dec) %>% arrange(desc(`Voting For`)) %>% head(18) %>% arrange(DuterTen, Alyansa, KiBam, Makabayan)


df <- cand %>%
  mutate(Voting_for_dec = `Voting For`/100) %>%
  arrange(DuterTen, Alyansa, KiBam, Makabayan) %>%
  mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
  select(-Voting_for_dec)

# corr_matrix <-block_corr(block_sizes=c(2, 2, 8, 6), rho_within=c(0, 0.9, 0.9, 0.9), rho_between=0.0)
corr_matrix <-block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0.0, 0.9, 0.9, 0.9, 0.9, 0.9), rho_between=0.0) # <- sample asymptotic neg rad
#corr_matrix <-block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0, 0.1, 0.5, 0.9, 0.9, 0.5), rho_between=0.0) 
# corr_matrix <-block_corr(block_sizes=c(2, 2, 8, 6), rho_within=c(0, 0.5, 0.5, 0.5), rho_between=0.0)
#corr_matrix <-block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0.5, 0.9, 0.9, 0.9, 0.9, 0.9), rho_between=0.0) 

set.seed(123974)
theta_hat <- (df$`Voting For`)/100
true_sds <- df$se
#true_sds <- rep(0.028/1.96, K)
K <- dim(df)[1]

variance_vector <- true_sds^2
delta <- diag(variance_vector)
varcovar_matrix <- delta^(1/2) %*% corr_matrix %*% delta^(1/2)
B <- 1000

alpha <- 0.05
S <- sqrt(diag(varcovar_matrix))

    
ci_methods <- list(
  nonrankbased = function() get_ci_nonrankbased(B = B,
                                                theta_hat = theta_hat,
                                                alpha = alpha,
                                                varcovar_matrix = varcovar_matrix),
  # rankbased_asymptotic = function() get_ci_rankbased_asymptotic(B = B,
  #                                                               theta_hat = theta_hat,
  #                                                               varcovar_matrix = varcovar_matrix,
  #                                                               alpha = alpha),
  # rankbased_level2bs = function() get_ci_rankbased_level2bs(B = B,
  #                                                           C = 300,
  #                                                           theta_hat = theta_hat,
  #                                                           varcovar_matrix = varcovar_matrix,
  #                                                           alpha = alpha),
  independent  = function() get_ci_independent(theta_hat = theta_hat, S = S, alpha = alpha),
  bonferroni   = function() get_ci_bonferroni(theta_hat = theta_hat, S = S, alpha = alpha)
)
ci_results <- lapply(ci_methods, function(f) f())

process_ci_result <- function(result, K) {
  tuple_list <- t(apply(
    data.frame(
      ci_lower = result$ci_lower,
      ci_upper = result$ci_upper
    ), 
    1, 
    function(row) as.numeric(row)
  ))
  
  print(
      sapply(1:K, function(x) 
    get_ranks(x, tuple_list)$ranks
  )
  )
  
  rank_range_length <- sapply(1:K, function(x) 
    length(get_ranks(x, tuple_list)$ranks)
  )
  list(
    t1 = get_t1(rank_range_length),
    t2 = get_t2(rank_range_length),
    t3 = get_t3(rank_range_length)
  )
}

# print("REACHED 3 ===================================")
processed <- lapply(ci_results, process_ci_result, K = K)
print("REACHED 4 ===================================")
res <- data.frame(
  t1_nonrankbased = processed$nonrankbased$t1,
  t2_nonrankbased = processed$nonrankbased$t2,
  t3_nonrankbased = processed$nonrankbased$t3,
  #coverage_nonrankbased = coverages$nonrankbased,
  # t1_rankbased_asymptotic = processed$rankbased_asymptotic$t1,
  # t2_rankbased_asymptotic = processed$rankbased_asymptotic$t2,
  # t3_rankbased_asymptotic = processed$rankbased_asymptotic$t3,
  # coverage_rankbased_asymptotic = coverages$rankbased_asymptotic,
  # t1_rankbased_level2bs = processed$rankbased_level2bs$t1,
  # t2_rankbased_level2bs = processed$rankbased_level2bs$t2,
  # t3_rankbased_level2bs = processed$rankbased_level2bs$t3,
  #coverage_rankbased_level2bs = coverages$rankbased_level2bs,
  t1_independent = processed$independent$t1,
  t2_independent = processed$independent$t2,
  t3_independent = processed$independent$t3,
  #coverage_independent = coverages$independent,
  t1_bonferroni = processed$bonferroni$t1,
  t2_bonferroni = processed$bonferroni$t2,
  t3_bonferroni = processed$bonferroni$t3
  #coverage_bonferroni = coverages$bonferroni
  )

summ <- as.data.frame(t(res))
summ$names <- rownames(summ)
rownames(summ) <- NULL
summ %>% rename(value = 'V1') %>%
  separate(
    col = names,
    into = c("metric", "approach"),
    sep = "_",
    extra = "merge"
  ) %>% arrange(metric, value)# %>%
  # filter(!(approach %in% c('rankbased_asymptotic', 'rankbased_level2bs')))
```


```{r}
cand
```


```{r}
seq(1,K, 1)
```

### Default viz

```{r warning = FALSE}
# kde_result <- output[[51]]
# df <- readRDS("../data/mean_travel_time_ranking_2011.rds")
cand$k <- seq(1,K, 1)
cand$sample_rank <- seq(1,K, 1)
cand$order_index <- seq(1,K, 1)

# kde_result <- merge(x = df[,c('k', 'iso', 'order_index')], y = kde_result, by = "k", all.x = TRUE)

library(ggplot2)
library(dplyr)
library(tidyr)

to_string_seq <- function(x, y){paste(seq(x, y, 1), collapse=',')}

dat_to_plot <- cand %>% 
    # select(c(k, iso, kde_rank_lower, kde_rank_upper, sample_rank, order_index,theta_k)) %>%
    select(c(k, `Rank LB`, `Rank UB`, sample_rank, order_index,
Candidate)) %>%
    mutate(string_ranks = mapply(to_string_seq, `Rank LB`, `Rank UB`)) %>%
    separate_rows(string_ranks, sep=",") %>%
    select(c(k, sample_rank, string_ranks, Candidate))

dat_to_plot$highlight <- ifelse(dat_to_plot$sample_rank == as.numeric(dat_to_plot$string_ranks), "highlight", "normal")

p <- ggplot(data = dat_to_plot, aes(x = reorder(k, Candidate),
                               y = as.numeric(string_ranks),
                               color = highlight)) + 
  geom_point(size = 1) +
  scale_color_manual(values = c("highlight" = "red", "normal" = "black")) +
  scale_y_continuous(breaks = 1:64) +
  labs(title='(Pulse Asia) visualization of the 95% joint confidence') + xlab('Candidate Index') + ylab('Sample rank') +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7),
        axis.text.y = element_text(size=4)
        ) +
  guides(colour="none") +
    theme(axis.line = element_line(colour = "gray"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),)

p
```


## Viz for nonrank


```{r}
process_ci_result <- function(result, K) {
  tuple_list <- t(apply(
    data.frame(
      ci_lower = result$ci_lower,
      ci_upper = result$ci_upper
    ), 
    1, 
    function(row) as.numeric(row)
  ))
  
  # print(
  #     sapply(1:K, function(x) 
  #   get_ranks(x, tuple_list)$ranks
  # )
  # )
  
  sapply(1:K, function(x) 
    64-get_ranks(x, tuple_list)$ranks+1
  )
}
```

```{r}
nonrankcand
```






```{r warning = FALSE}
nonrankcand <- cand %>%
  mutate(Voting_for_dec = `Voting For`/100) %>%
  mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
  select(-Voting_for_dec) %>% arrange(desc(`Voting For`)) %>%  arrange(DuterTen, Alyansa, KiBam, Makabayan) 

nonrankcand$`Rank LB` <- sapply(process_ci_result(result = ci_results$nonrankbased, K=64), min)
nonrankcand$`Rank UB` <- sapply(process_ci_result(result = ci_results$nonrankbased, K=64), max)
nonrankcand <- nonrankcand %>% arrange(desc(`Voting For`))

# kde_result <- output[[51]]
K=64
# df <- readRDS("../data/mean_travel_time_ranking_2011.rds")
nonrankcand$k <- seq(1,K, 1)
nonrankcand$sample_rank <- seq(1,K, 1)
nonrankcand$order_index <- seq(1,K, 1)

# kde_result <- merge(x = df[,c('k', 'iso', 'order_index')], y = kde_result, by = "k", all.x = TRUE)

library(ggplot2)
library(dplyr)
library(tidyr)

to_string_seq <- function(x, y){paste(seq(x, y, 1), collapse=',')}

dat_to_plot <- nonrankcand %>% 
    # select(c(k, iso, kde_rank_lower, kde_rank_upper, sample_rank, order_index,theta_k)) %>%
    select(c(k, `Rank LB`, `Rank UB`, sample_rank, order_index,
Candidate)) %>%
    mutate(string_ranks = mapply(to_string_seq, `Rank LB`, `Rank UB`)) %>%
    separate_rows(string_ranks, sep=",") %>%
    select(c(k, sample_rank, string_ranks, Candidate))

dat_to_plot$highlight <- ifelse(dat_to_plot$sample_rank == as.numeric(dat_to_plot$string_ranks), "highlight", "normal")

p <- ggplot(data = dat_to_plot, aes(x = reorder(k, Candidate),
                               y = as.numeric(string_ranks),
                               color = highlight)) + 
  geom_point(size = 1) +
  scale_color_manual(values = c("highlight" = "red", "normal" = "black")) +
  scale_y_continuous(breaks = 1:64) +
  labs(title='(Nonrank) visualization of the 95% joint confidence') + xlab('Candidate Index') + ylab('Sample rank') +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7),
        axis.text.y = element_text(size=4)
        ) +
  guides(colour="none") +
    theme(axis.line = element_line(colour = "gray"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),)

p
```


```{r warning = FALSE}
independentcand <- cand %>%
  mutate(Voting_for_dec = `Voting For`/100) %>%
  mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
  select(-Voting_for_dec) %>% arrange(desc(`Voting For`)) %>%  arrange(DuterTen, Alyansa, KiBam, Makabayan) 

independentcand$`Rank LB` <- sapply(process_ci_result(result = ci_results$bonferroni, K=64), min)
independentcand$`Rank UB` <- sapply(process_ci_result(result = ci_results$bonferroni, K=64), max)
independentcand <- nonrankcand %>% arrange(desc(`Voting For`))

# kde_result <- output[[51]]
K=64
# df <- readRDS("../data/mean_travel_time_ranking_2011.rds")
independentcand$k <- seq(1,K, 1)
independentcand$sample_rank <- seq(1,K, 1)
independentcand$order_index <- seq(1,K, 1)

# kde_result <- merge(x = df[,c('k', 'iso', 'order_index')], y = kde_result, by = "k", all.x = TRUE)

library(ggplot2)
library(dplyr)
library(tidyr)

to_string_seq <- function(x, y){paste(seq(x, y, 1), collapse=',')}

dat_to_plot <- independentcand %>% 
    # select(c(k, iso, kde_rank_lower, kde_rank_upper, sample_rank, order_index,theta_k)) %>%
    select(c(k, `Rank LB`, `Rank UB`, sample_rank, order_index,
Candidate)) %>%
    mutate(string_ranks = mapply(to_string_seq, `Rank LB`, `Rank UB`)) %>%
    separate_rows(string_ranks, sep=",") %>%
    select(c(k, sample_rank, string_ranks, Candidate))

dat_to_plot$highlight <- ifelse(dat_to_plot$sample_rank == as.numeric(dat_to_plot$string_ranks), "highlight", "normal")

p <- ggplot(data = dat_to_plot, aes(x = reorder(k, Candidate),
                               y = as.numeric(string_ranks),
                               color = highlight)) + 
  geom_point(size = 1) +
  scale_color_manual(values = c("highlight" = "red", "normal" = "black")) +
  scale_y_continuous(breaks = 1:64) +
  labs(title='(Pulse Asia) visualization of the 95% joint confidence') + xlab('Candidate Index') + ylab('Sample rank') +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7),
        axis.text.y = element_text(size=4)
        ) +
  guides(colour="none") +
    theme(axis.line = element_line(colour = "gray"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),)

p
```










































Result becomes affected by the sign and this case matters when there are small 
proportions which make it more possible to sample negative values from `mvrnorm`

Given `-0.1` and `0.001`

```{r}
# sort before square (ito yung nasa current code)
(sort(c(-0.1, 0.001)))^2
```

```{r}
# square before sort
sort(c((-0.1)^2, 0.001^2))
```



```{r}
(0.002342546)^2 # 5.487523e-06 

(0.002342546)^2 + 4.145833e-06 # 2.206456e-05

(0.002342546)^2 + 4.145833e-06 - 1.085773e-04
```



```{r}
(0.0002075621)^2 # 4.308204e-08

(0.0002075621)^2+ 4.145833e-06# 2.535582e-06

(0.0002075621)^2+ 2.492500e-06 -1.969182e-05
```


```{r}
#(-0.0001323539)^2 + 2.492500e-06 ##- (-0.001639273)^2

#1.751757e-08 = (-0.0001323539)^2
```
```{r}
(-0.001639273)^2
```


```{r}
(0.028/1.96)^2
```



```{r}
process_ci_result <- function(result, K) {
  tuple_list <- t(apply(
    data.frame(
      ci_lower = result$ci_lower,
      ci_upper = result$ci_upper
    ), 
    1, 
    function(row) as.numeric(row)
  ))
  
  return(tuple_list)
}

process_ci_result(res, K)
```




```{r}
((1.712325e-04) + (0.2596490)^2) 
```
0.06758881

```{r}
K = 64
alpha = 0.05
1-(1-alpha)^(1/K)
```




```{r}
source("R/simulate/compute_ci.R")
source("R/simulate/compute_metrics.R")

df <- cand %>% 
  mutate(Voting_for_dec = `Voting For`/100) %>%
  mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
  select(-Voting_for_dec) %>% arrange(desc(`Voting For`)) %>% head(18) %>% arrange(DuterTen, Alyansa, KiBam, Makabayan)


corr_matrix <-block_corr(block_sizes=c(2, 2, 8, 6), rho_within=c(0, 0.5, 0.5, 0.5), rho_between=0.0)
#corr_matrix <-block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0.5, 0.9, 0.9, 0.9, 0.9, 0.9), rho_between=0.0) 
#corr_matrix <-block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0, 0.1, 0.5, 0.9, 0.9, 0.5), rho_between=0.0) 

set.seed(123974)
theta_hat <- df$`Voting For`/100
true_sds <- df$se
variance_vector <- true_sds^2
delta <- diag(variance_vector)
varcovar_matrix <- delta^(1/2) %*% corr_matrix %*% delta^(1/2)
B=5000
K=18
alpha=0.05
```



```{r}
source("R/simulate/compute_metrics.R")
library(doParallel)
cl=parallel::makeCluster(15)
registerDoParallel(cl)
case_start <- Sys.time()


df <- cand %>% arrange(DuterTen, Alyansa, KiBam, Makabayan) %>% 
  mutate(Voting_for_dec = `Voting For`/100) %>%
  mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
  select(-Voting_for_dec)
# mean <- 23.8
# sds <- c(2)#c(3.6, 6.0)
Ks <- c(dim(df)[1])#c(40,50)
# corr <- c(0.1, 0.5, 0.9)

print(cat("RESULTS FOR SD =",sd, "; K =", K))

# none, mkbyn,kibam, alyansa, duterte, alyansa&duterte
corr_matrix <- block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0, 0.8, 0.8, 0.8, 0.8, 0.8), rho_between=0.0) 
#corr_matrix <-block_corr(block_sizes=c(27, 11, 2, 10, 12, 2), rho_within=c(0, 0.1, 0.5, 0.9, 0.9, 0.5), rho_between=0.0) 

set.seed(123974)
true_theta <- df$`Voting For`
true_sds <- df$se
variance_vector <- true_sds^2
delta <- diag(variance_vector)
varcovar_matrix <- delta^(1/2) %*% corr_matrix %*% delta^(1/2)
out <- implement_algorithm2(
    true_theta = true_theta,
    K = K, 
    reps=5000, # step 4
    B=500,#700, 
    alpha= 0.05,
    C=300,#350,
    varcovar_matrix = varcovar_matrix)
case <- paste(paste0("K",gsub("\\.", "p", as.character(K))),
        paste0("r",gsub("\\.", "p", "pulse")), #as.character(r))),
#          paste0("r",gsub("\\.", "p", "unbalanced-block-high")), #as.character(r))),
        sep = "_")
case_end <- Sys.time()
        case_runtime <- as.numeric(difftime(case_end, case_start, units = "mins"))
        cat("Finished at:", format(case_end, "%I:%M %p"), "\n")
        cat("Runtime for", case, round(case_runtime, 2), "minutes\n")

print(colMeans(out))
filename <- paste0(
  case,
  ".rds")

saveRDS(out, file = filename)
stopCluster(cl)
```



# Run Simulation from notebook

```{r}
source("R/simulate/compute_metrics.R")
library(doParallel)
cl=parallel::makeCluster(15)
registerDoParallel(cl)
case_start <- Sys.time()


df <- readRDS("data/mean_travel_time_ranking_2011.rds")
mean <- 23.8
sds <- c(2)#c(3.6, 6.0)
Ks <- c(40,50)
# corr <- c(0.1, 0.5, 0.9)

for (sd in sds) {
  for (K in Ks) {
  print(cat("RESULTS FOR SD =",sd, "; K =", K))
  corr_matrix <-block_corr(block_sizes=c(.2*K,.3*K, .5*K), rho_within=c(0.1, 0.5, 0.9), rho_between=0.0)# block_corr(block_sizes=c(0.3*K,0.7*K), rho_within=c(0.9, 0.1), rho_between=0.0) #  block_corr(block_sizes=c(5,5), rho_within=c(0.75, 0.15), rho_between=0.0) #block_corr(block_sizes=c(5,5), rho_within=c(0.85, 0.25), rho_between=0.0)# (1 - r) * diag(K) + r * matrix(1, K, K)

  set.seed(123974)
  true_theta <- rnorm(K, mean, sd)
  true_sds <- df$S[1:K]
  variance_vector <- true_sds^2
  delta <- diag(variance_vector)
  varcovar_matrix <- delta^(1/2) %*% corr_matrix %*% delta^(1/2)
  out <- implement_algorithm2(
      true_theta = true_theta,
      K = K, 
      reps=5000, # step 4
      B=500,#700, 
      alpha= 0.05,
      C=300,#350,
      varcovar_matrix = varcovar_matrix)
  case <- paste(paste0("K",gsub("\\.", "p", as.character(K))),
          paste0("sd",gsub("\\.", "p", as.character(sd))),
          paste0("r",gsub("\\.", "p", "unbalanced-block-high")), #as.character(r))),
#          paste0("r",gsub("\\.", "p", "unbalanced-block-high")), #as.character(r))),
          sep = "_")
  case_end <- Sys.time()
          case_runtime <- as.numeric(difftime(case_end, case_start, units = "mins"))
          cat("Finished at:", format(case_end, "%I:%M %p"), "\n")
          cat("Runtime for", case, round(case_runtime, 2), "minutes\n")
  
  print(colMeans(out))
  filename <- paste0(
    case,
    ".rds")
  
  saveRDS(out, file = filename)
}
}
stopCluster(cl)
```




# Create summary file per case

```{r}
# Source - https://stackoverflow.com/a/63126233
# Posted by heds1
# Retrieved 2026-01-05, License - CC BY-SA 4.0

base_dir <- './simulation_results/unbalanced_three_high/'
all_files <- paste0(base_dir, 
                    list.files(base_dir, pattern = "\\.rds$", 
                               recursive = FALSE))

summarize_means <- function(file){
  dat <- readRDS(file)
  summary <- colMeans(dat)
  return(summary)
  #summary['file'] = file
  #return(t(as.data.frame(summary)))
}

df <- as.data.frame(do.call("rbind", lapply(all_files, summarize_means)))
df$file <-all_files
df$file
```


```{r}
library(tidyr)
library(dplyr)
# df %>% separate(file, sep = "_", into = c("K", "sd", 'r')) #%>% mutate(sd = sd.replace)
```


```{r}
df$file <- sub("simulation_results/unbalanced_three_high/", "", df$file)
df
```


```{r}
summ <- df %>% separate(file, sep = "_", into = c("K", "sd", 'r'))
# sub("sd", "", summ$sd)
summ
```

```{r}
# Source - https://stackoverflow.com/a/55986799
# Posted by G. Grothendieck, modified by community. See post 'Timeline' for change history
# Retrieved 2026-01-05, License - CC BY-SA 4.0
summ <- df %>% separate(file, sep = "_", into = c("K", "sd", 'r'))

summ$sd <- sub("sd", "", summ$sd) 
summ$sd <- sub("p", ".", summ$sd) 
summ$K <- sub("./K", "", summ$K) 
summ$r <- sub("r", "", summ$r) 
summ$r <- sub(".rds", "", summ$r) 
summ$r <- sub("p", ".", summ$r) 
summary <- summ %>%  mutate(sd = as.numeric(sd)) %>%  
  # mutate(r = as.numeric(r)) %>%  
  mutate(r = r) %>%  
  mutate(K = as.numeric(K))

summary

# 
summary_form <- summary %>% pivot_longer(
    cols = `t1_nonrankbased`:`coverage_bonferroni`,
    names_to = "metric",
    values_to = "value"
) %>%
  separate(metric, into=c("metric", "approach"), extra = "merge", sep = "_") %>%
  pivot_wider(names_from = "approach", values_from = "value")

summary_form
write.csv(summary_form, "summary_3unbalanced-high.csv")
```

# Scratch papers {.hidden}

```{r}
source("R/simulate/compute_metrics.R")
# library(doParallel)
# cl=parallel::makeCluster(15)
# registerDoParallel(cl)
# case_start <- Sys.time()

library("ggplot2")

df <- readRDS("data/mean_travel_time_ranking_2011.rds")
mean <- 23.8
sds <- c(2, 3.6, 6.0)
Ks <- c(10, 20, 30, 40, 50)
# corr <- c(0.1, 0.5, 0.9)
data_list <- list()

for (sd in sds) {
  for (K in Ks) {
  print(cat("RESULTS FOR SD =",sd, "; K =", K))
  corr_matrix <-block_corr(block_sizes=c(.2*K,.3*K, .5*K), rho_within=c(0.1, 0.5, 0.9), rho_between=0.0)# block_corr(block_sizes=c(0.3*K,0.7*K), rho_within=c(0.9, 0.1), rho_between=0.0) #  block_corr(block_sizes=c(5,5), rho_within=c(0.75, 0.15), rho_between=0.0) #block_corr(block_sizes=c(5,5), rho_within=c(0.85, 0.25), rho_between=0.0)# (1 - r) * diag(K) + r * matrix(1, K, K)

  set.seed(123974)
  true_theta <- rnorm(K, mean, sd)
  data_list[[length(data_list) + 1]] <- data.frame(sd = sd, K = K, true_theta = true_theta)
  }}

data_list
```



```{r}
data_list %>% 
  bind_rows()
```

```{r}
library("ggplot2")

df <- readRDS("data/mean_travel_time_ranking_2011.rds")
mean <- 23.8
sds <- c(2, 3.6, 6.0)
Ks <- c(10, 20, 30, 40, 50)
# corr <- c(0.1, 0.5, 0.9)
data_list <- list()

for (sd in sds) {
  for (K in Ks) {
  print(cat("RESULTS FOR SD =",sd, "; K =", K))
  corr_matrix <-block_corr(block_sizes=c(.2*K,.3*K, .5*K), rho_within=c(0.9, 0.5, 0.1), rho_between=0.0)
  # block_corr(block_sizes=c(0.3*K,0.7*K), rho_within=c(0.9, 0.1), rho_between=0.0) 
  #  block_corr(block_sizes=c(5,5), rho_within=c(0.75, 0.15), rho_between=0.0) 
  #block_corr(block_sizes=c(5,5), rho_within=c(0.85, 0.25), rho_between=0.0)# (1 - r) * diag(K) + r * matrix(1, K, K)

  set.seed(123974)
  true_theta <- rnorm(K, mean, sd)
  data_list[[length(data_list) + 1]] <- data.frame(sd = sd, K = K, true_theta = true_theta)
  }}

data_list %>% 
  bind_rows() %>% 
  mutate(data_spread = factor(ifelse(sd == 2, "low", 
                              ifelse(sd == 3.6, "medium", "high")),
                              levels =c("low", 'medium', 'high'),
                              ordered =TRUE
                              )) %>%
  ggplot(.,
         aes(x = data_spread,
             y = true_theta)) +
  facet_wrap(~K, ncol=5) +
  labs(title = expression(True~theta~Values~Used~'in'~Simulation),
       x = expression(theta~Variability),
       y = expression(theta)) +
  geom_boxplot() +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```



```{r}
corr <- 0.9
corr_matrix <- (1 - corr) * diag(K) + corr * matrix(1, K, K)
# variance_vector <- true_sds^2
# delta <- diag(variance_vector)
# varcovar_matrix <- delta^(1/2) %*% corr_matrix %*% delta^(1/2)
# varcovar_matrix

K <- 50
corr <- 0.1
for (K in c(10,20,30,40,50)) {
  block_unb <- (1 - corr) * diag(K) + corr * matrix(1, K, K)
  tol = 1e-8
  eval <- eigen(block_unb)$values
  print(paste("PD for K=",K, ":", all(eval > -abs(tol * max(eval)))))
}
```




```{r}
# source("R/compute_metrics.R")
# stopImplicitCluster()
# library(doRNG)
# registerDoSEQ()
# 
# df <- readRDS("data/mean_travel_time_ranking_2011.rds")
# mean <- 23.8
# sds <- c(2, 3.6, 6)
# K <- c(10)#(51, 40, 30, 20, 10, 5)
# corr <- c(0.1,0.5)
# 
# for (sd in sds) {
#   for (r in corr) {
#   print(cat("RESULTS FOR SD",sd, 'CORRELATION', r))
#   corr_matrix <- (1 - r) * diag(K) + r * matrix(1, K, K)
# 
#   set.seed(123974)
#   true_theta <- rnorm(K, mean, sd)
#   print(true_theta)
#   print(true_sds)
#   true_sds <- df$S[1:K]
#   variance_vector <- true_sds^2
#   delta <- diag(variance_vector)
#   varcovar_matrix <- delta^(1/2) %*% corr_matrix %*% delta^(1/2)
#   out <- implement_algorithm2(
#       true_theta = true_theta,
#       K = K, 
#       reps=2, # step 4
#       B=10, 
#       alpha= 0.05,
#       C=6,
#       varcovar_matrix = varcovar_matrix)
#   case_end <- Sys.time()
#           case_runtime <- as.numeric(difftime(case_end, case_start, units = "mins"))
#           cat("Finished at:", format(case_end, "%I:%M %p"), "\n")
#           cat("Runtime for this case:", round(case_runtime, 2), "minutes\n")
#   
#   # print(colMeans(out))
#   filename <- paste0(
#     paste(paste0("K",gsub("\\.", "p", as.character(K))),
#           paste0("sd",gsub("\\.", "p", as.character(sd))),
#           paste0("r",gsub("\\.", "p", as.character(r))),
#           sep = "_"),
#     ".rds")
#   
#   # saveRDS(out, file = filename)
# }
# }
# 
# # stopCluster(cl)
# #1.964865
# 
# # 1.964873 mali
```






