
\begin{table}[H]
\centering
{\fontsize{13pt}{17pt}\selectfont 
\begin{tabular}{p{11cm} p{4cm}}
\hline
$\boldsymbol{\theta}$ & $\mathbf{R}$ \\
\hline
\hline

\multicolumn{2}{c}{\textbf{K = 10}} \\
\hline
\multirow{3}{11cm}{(22.5, 24.9, 27.5, 24.3, 24.8, 23.2, 23, 21.6, 25.1, 19)$'$} 
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
\hline
\multirow{3}{11cm}{(21.5, 25.7, 30.5, 24.7, 25.5, 22.6, 22.3, 19.9, 26.1, 15.2)$'$} 
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\

\hline
\multirow{3}{11cm}{(19.9, 27, 34.9, 25.3, 26.7, 21.9, 21.3, 17.3, 27.7, 9.4)$'$} 
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
\hline
\multicolumn{2}{c}{\textbf{K = 20}} \\
\hline
\multirow{3}{11cm}{(22.5, 24.9, 27.5, 24.3, 24.8, 23.2, 23, 21.6, 25.1, 19, 21.3, 24.1, 26.5, 26.9, 23.2, 25.8, 21.8, 21.6, 25.6, 21.2)$'$} 
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
& \\
\hline
\multirow{3}{11cm}{(21.5, 25.7, 30.5, 24.7, 25.5, 22.6, 22.3, 19.9, 26.1, 15.2, 19.3, 24.3, 28.7, 29.3, 22.7, 27.5, 20.1, 19.9, 27.1, 19.1)$'$} 
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
& \\
\hline
\multirow{3}{11cm}{(19.9, 27, 34.9, 25.3, 26.7, 21.9, 21.3, 17.3, 27.7, 9.4, 16.2, 24.6, 31.9, 33, 21.9, 29.9, 17.7, 17.3, 29.3, 16)$'$} 
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
& \\
\hline
\multicolumn{2}{c}{\textbf{K = 30}} \\
\hline
\multirow{4}{*}{%
  \parbox{11cm}{%
  \vspace{0.2cm}
    (22.5, 24.9, 27.5, 24.3, 24.8, 23.2, 23, 21.6, 25.1, 19, 
    21.3, 24.1, 26.5, 26.9, 23.2, 25.8, 21.8, 21.6, 25.6, 21.2, 
    25.7, 22.2, 22.7, 22.6, 21.9, 24.2, 23.6, 22, 24.5, 25)$'$
    \vspace{0.2cm}
  }%
} 
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
& \\
& \\
\hline
\multirow{4}{*}{%
  \parbox{11cm}{%
  \vspace{0.2cm}
  (21.5, 25.7, 30.5, 24.7, 25.5, 22.6, 22.3, 19.9, 26.1, 15.2, 19.3, 24.3, 28.7, 29.3, 22.7, 27.5, 20.1, 19.9, 27.1, 19.1, 27.2, 20.9, 21.8, 21.7, 20.4, 24.5, 23.5, 20.5, 25.1, 26)$'$
    \vspace{0.2cm}
  }%
} 
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
& \\
& \\
\hline
\multirow{4}{*}{%
  \parbox{11cm}{%
  \vspace{0.2cm}
  (19.9, 27, 34.9, 25.3, 26.7, 21.9, 21.3, 17.3, 27.7, 9.4, 16.2, 24.6, 31.9, 33, 21.9, 29.9, 17.7, 17.3, 29.3, 16, 29.4, 19, 20.4, 20.3, 18.2, 25, 23.3, 18.3, 26, 27.4)$'$
    \vspace{0.2cm}
  }%
} 
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
& \\
& \\
\hline
\end{tabular}
}
\end{table}





\begin{table}[H]
\centering
{\fontsize{13pt}{17pt}\selectfont 
\begin{tabular}{p{11cm} p{4cm}}
\hline
$\boldsymbol{\theta}$ & $\mathbf{R}$ \\
\hline
\hline
\multicolumn{2}{c}{\textbf{K = 40}} \\
\hline
\multirow{6}{11cm}{(22.5, 24.9, 27.5, 24.3, 24.8, 23.2, 23, 21.6, 25.1, 19, 21.3, 24.1, 26.5, 26.9, 23.2, 25.8, 21.8, 21.6, 25.6, 21.2, 25.7, 22.2, 22.7, 22.6, 21.9, 24.2, 23.6, 22, 24.5, 25, 26.5, 25.1, 25.2, 27.1, 25.3, 22.8, 20.6, 21.1, 26, 26)$'$}
&  \\
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
&  \\
&  \\
&  \\
\hline
\multirow{6}{11cm}{(21.5, 25.7, 30.5, 24.7, 25.5, 22.6, 22.3, 19.9, 26.1, 15.2, 19.3, 24.3, 28.7, 29.3, 22.7, 27.5, 20.1, 19.9, 27.1, 19.1, 27.2, 20.9, 21.8, 21.7, 20.4, 24.5, 23.5, 20.5, 25.1, 26, 28.6, 26.1, 26.4, 29.7, 26.5, 22.1, 18, 18.9, 27.8, 27.8)$'$}
&  \\
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
&  \\
&  \\
&  \\
\hline
\multirow{6}{11cm}{(19.9, 27, 34.9, 25.3, 26.7, 21.9, 21.3, 17.3, 27.7, 9.4, 16.2, 24.6, 31.9, 33, 21.9, 29.9, 17.7, 17.3, 29.3, 16, 29.4, 19, 20.4, 20.3, 18.2, 25, 23.3, 18.3, 26, 27.4, 31.9, 27.7, 28.1, 33.6, 28.2, 20.9, 14.1, 15.6, 30.5, 30.5)$'$}
&  \\
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
&  \\
&  \\
&  \\
\hline
\multicolumn{2}{c}{\textbf{K = 50}} \\
\hline
\multirow{6}{11cm}{(22.5, 24.9, 27.5, 24.3, 24.8, 23.2, 23, 21.6, 25.1, 19, 21.3, 24.1, 26.5, 26.9, 23.2, 25.8, 21.8, 21.6, 25.6, 21.2, 25.7, 22.2, 22.7, 22.6, 21.9, 24.2, 23.6, 22, 24.5, 25, 26.5, 25.1, 25.2, 27.1, 25.3, 22.8, 20.6, 21.1, 26, 26, 22.1, 21.4, 23.2, 22.3, 22.4, 23.1, 21.4, 24.8, 27, 23.4)$'$}
&  \\
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
&  \\
&  \\
&  \\
&  \\
\hline
\multirow{6}{11cm}{(21.5, 25.7, 30.5, 24.7, 25.5, 22.6, 22.3, 19.9, 26.1, 15.2, 19.3, 24.3, 28.7, 29.3, 22.7, 27.5, 20.1, 19.9, 27.1, 19.1, 27.2, 20.9, 21.8, 21.7, 20.4, 24.5, 23.5, 20.5, 25.1, 26, 28.6, 26.1, 26.4, 29.7, 26.5, 22.1, 18, 18.9, 27.8, 27.8, 20.8, 19.5, 22.8, 21.2, 21.3, 22.5, 19.5, 25.5, 29.6, 23)$'$}
&  \\
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
&  \\
&  \\
&  \\
&  \\
\hline
\multirow{6}{11cm}{(19.9, 27, 34.9, 25.3, 26.7, 21.9, 21.3, 17.3, 27.7, 9.4, 16.2, 24.6, 31.9, 33, 21.9, 29.9, 17.7, 17.3, 29.3, 16, 29.4, 19, 20.4, 20.3, 18.2, 25, 23.3, 18.3, 26, 27.4, 31.9, 27.7, 28.1, 33.6, 28.2, 20.9, 14.1, 15.6, 30.5, 30.5, 18.8, 16.6, 22.1, 19.4, 19.6, 21.6, 16.7, 26.7, 33.5, 22.5)$'$}
&  \\
& $\mathbf{R}_{\text{eq}}, \rho = 0.1, 0.5, 0.9$ \\
& $\mathbf{R}_{\text{block}}$ - \text{2, 3 blocks} \\
&  \\
&  \\
&  \\
&  \\
\hline
\end{tabular}
}
\end{table}









library(kableExtra)

FONT_SIZE <- 11


create_basic_results_table <- function(dataset, caption){
  # kable(
  # get_tmeasures_for_app_data(ci_results),
  # "latex",
  # booktabs = TRUE,
  # escape = FALSE,
  # linesep = "",
  # longtable = TRUE,
  # caption = caption) %>%
  # kable_styling(
  #   latex_options = c("striped", "repeat_header", "HOLD_position"),
  #   stripe_color = "gray!15",
  #   font_size=FONT_SIZE
  # )
  dataset %>% kable("latex",
                     booktabs = TRUE,
                     escape = FALSE,
                     linesep = "",
                     longtable = TRUE,
                     align = "c",
                     # col.names = c(vector_1,
                     #               selected_columns),
                     caption = caption) %>%
    collapse_rows(columns = c(1,2),
                  valign = "middle", 
                  latex_hline = "major")%>%
    kable_styling(latex_options = c(
      "repeat_header", 
      "HOLD_position"),
      #stripe_color = "gray!15",
      #stripe_index = striped,
      font_size=FONT_SIZE)
}

# create_table_for_true_theta <- function(dataset){
#   return(kable(
#     dataset %>% 
#       select(K, true_theta, R), 
#     "latex",
#     booktabs = TRUE,
#     escape = FALSE,
#     linesep = "",
#     longtable = TRUE,
#     col.names = c("K", '$\\boldsymbol{\\theta}$', "R")) %>%
#       column_spec(1, width = "0.75cm") %>%
#       column_spec(3, width = "4cm") %>%
#       column_spec(2, width = "11cm") %>%
#       kable_styling(
#         latex_options = c("striped", "repeat_header", "HOLD_position"),
#         stripe_color = "gray!15",
#         font_size=FONT_SIZE
#     )
#   )
# }

create_table_for_true_theta <- function(dataset){
  # 1. Remove K from the display but keep it for logic
  display_data <- dataset %>% select(true_theta, R)
  
  # 2. Identify where to pack (every 3 rows)
  # This assumes your data is already sorted by K
  k_values <- unique(dataset$K)
  num_k <- length(k_values)
  
  tbl <- kable(
    display_data, 
    "latex",
    booktabs = TRUE,
    escape = FALSE,
    linesep = "\\addlinespace[0.5em]\\midrule\\addlinespace[0.5em]",
    longtable = TRUE,
    col.names = c('$\\boldsymbol{\\theta}$', "R") # Removed K from header
  ) %>%
    # Adjust widths (removed spec for col 1 since K is gone)
    column_spec(1, width = "12cm") %>%
    column_spec(2, width = "4cm") %>%
    kable_styling(
      latex_options = c("repeat_header"), # Removed HOLD_position (incompatible with longtable)
      # stripe_color = "gray!15",
      font_size = FONT_SIZE
    )
  
  # 3. Dynamically pack rows in batches of 3
  for(i in 1:num_k) {
    start_row <- (i - 1) * 3 + 1
    end_row <- i * 3
    label <- paste0("K = ", k_values[i])
    tbl <- tbl %>% pack_rows(label, start_row, end_row, 
                                   latex_align = "l",        # Left-align headers (usually cleaner)
                                   indent = FALSE,           # NO indents for cell content
                                   latex_gap_space = "0em",  # Extra air between groups
                                   bold = TRUE,              # Make K stand out
                                   background = "#eeeeee")   # Subtle gray bar for the group header
  }
  
  return(tbl)
}


create_table_for_tightness_measure <- function(summary, metric_type,
                                               equicorrelation){
  
  # if (unordered) {
  unord <- c("Ind","Bonf","NR")
  ord <- c("Asymp","Boot")
  colwidth  <- "0.8cm"
  # } else {
  #   selected_columns <- c("Asymptotic Var","Bootstrap Est")
  #   colwidth  <- "3cm"
  # }
  
  num <- length(c(ord,unord))
  
  # sd <- c("Low $\\\\boldsymbol{\\\\theta}$ Variability" = 3, 
  #         "Moderate $\\\\boldsymbol{\\\\theta}$ Variability" = 3, 
  #         "High $\\\\boldsymbol{\\\\theta}$ Variability" = 3,
  #         "Low $\\\\boldsymbol{\\\\theta}$ Variability" = 2, 
  #         "Moderate $\\\\boldsymbol{\\\\theta}$ Variability" = 2, 
  #         "High $\\\\boldsymbol{\\\\theta}$ Variability" = 2)
  
  sd <- c("Low" = 3, 
          "Moderate" = 3, 
          "High" = 3,
          "Low" = 2, 
          "Moderate" = 2, 
          "High" = 2)
  approach <- c(" " = 2,c("Unordered" = 9, "Ordered" = 6))
  
  if (equicorrelation) {
    vector_1 <- c("K", "r")
    striped <- c(2:4, 8:10, 14:16)#rep(c(0, 6, 12), each = 3) + 1:3
    headers <- c(" " = 2, sd)
  } else {
    vector_1 <- c("K")
    striped <- -1 #rep(c(0, 10), each = 5) + 1:5
    headers <- c(" "= 1, sd)
  }

# create_table_for_tightness_measure <- function(summary, metric_type,
#                                                equicorrelation,
#                                                unordered = TRUE){
# 
#   if (unordered) {
#     selected_columns <- c("Independent","Bonferroni","Nonrank")
#     colwidth  <- "2cm"
#   } else {
#     selected_columns <- c("Asymptotic Var","Bootstrap Est")
#     colwidth  <- "3cm"
#   }
#   num <- length(selected_columns)
#   if (equicorrelation) {
#     vector_1 <- c("K", "r")
#     striped <- rep(c(0, 6, 12), each = 3) + 1:3
#     headers <- c(" " = 2, 
#                  "Low $\\\\boldsymbol{\\\\theta}$ Variability" = num, 
#                  "Moderate $\\\\boldsymbol{\\\\theta}$ Variability" = num, 
#                  "High $\\\\boldsymbol{\\\\theta}$ Variability" = num)
#   } else {
#     vector_1 <- c("K")
#     striped <- -1 #rep(c(0, 10), each = 5) + 1:5
#     headers <- c(" "=1,
#                  "Low $\\\\boldsymbol{\\\\theta}$ Variability" = num, 
#                  "Moderate $\\\\boldsymbol{\\\\theta}$ Variability" = num,
#                  "High $\\\\boldsymbol{\\\\theta}$ Variability" = num)
#   }

  
  formatted <- summary %>%
    kable("latex",
          booktabs = TRUE,
          escape = FALSE,
          linesep = "",
          longtable = TRUE,
          col.names = c(vector_1, 
                        c(rep(unord,3),rep(ord,3))),
          caption = paste("Simulation Results for Tightness Measure", 
                          metric_type)) %>%
    collapse_rows(columns = 1,
                  valign = "middle", 
                  latex_hline = "none",
                  row_group_label_position = "first") %>%
    add_header_above(headers, escape = FALSE) %>%
    add_header_above(approach, escape = FALSE) %>%
    kable_styling(latex_options = c("striped",
                                    "repeat_header",
                                    "HOLD_position"),
                  font_size=FONT_SIZE-1,
                  stripe_color = "gray!15",
                  stripe_index = striped)
                    #rep(c(0, 6, 12), each = 3) + 1:3) %>%

  if (equicorrelation) {
    final <- formatted %>% 
      column_spec(1:2, width = "0.5cm") %>%
      column_spec(3:(2+3*num), width = colwidth)
  } else {
    final <- formatted %>% 
      column_spec(1:1, width = "1cm") %>%
      column_spec(2:(1+3*num), width = colwidth) %>%
      pack_rows("2 balanced blocks", 1, 5,
                latex_gap_space = "0.3em") %>%
      pack_rows("2 unbalanced blocks", 6, 10,
                latex_gap_space = "0.3em") %>%
      pack_rows("3 unbalanced blocks - low", 11, 15,
                latex_gap_space = "0.3em") %>%
      pack_rows("3 unbalanced block - high", 16, 20,
                latex_gap_space = "0.3em")
  }
  return(
    final
  )
}

create_table_for_coverage <- function(summary, footnote, equicorrelation = TRUE,
                                      unordered = TRUE){
  
  if (equicorrelation) {
    vector_1 <- c("K", "r")
    striped <- rep(c(0, 6, 12), each = 3) + 1:3
  } else {
    vector_1 <- c("K")
    striped <- -1
  }
  
  if (unordered) {
    selected_columns <- c("Independent","Bonferroni","Nonrank")
    colwidth  <- "3cm"
  } else {
    selected_columns <- c("Asymptotic Variance","Bootstrap Estimate")
    colwidth  <- "4cm"
  }
  num <- length(selected_columns)
  formatted <- summary %>%
    kable("latex",
          booktabs = TRUE,
          escape = FALSE,
          linesep = "",
          longtable = TRUE,
          align = "c",
          col.names = c(vector_1,
                        selected_columns),
          caption = "Simulation Results for Coverage Probabilities")

  if (equicorrelation) {
    final <- formatted %>% 
      column_spec(1:2, width = "1cm") %>%
      column_spec(3:(2+num), width = colwidth)
  } else {
    final <- formatted %>% 
      column_spec(1:1, width = "1cm") %>%
      column_spec(2:(1+num), width = colwidth) %>%
      pack_rows("2 balanced blocks", 1, 5) %>%
      pack_rows("2 unbalanced blocks", 6, 10) %>%
      pack_rows("3 unbalanced blocks - low", 11, 15) %>%
      pack_rows("3 unbalanced block - high", 16, 20) 
  }
  
  return(
    final %>% 
      collapse_rows(columns = 1,
                    valign = "middle", 
                    latex_hline = "none",
                    row_group_label_position = "first") %>%
      kable_styling(latex_options = c("striped", 
                                      "repeat_header", 
                                      "HOLD_position"),
                    stripe_color = "gray!15",
                    stripe_index = striped,
                    font_size=FONT_SIZE) %>%
    footnote(general_title = "\\\\footnotesize\\\\textit{Note: }", 
             footnote_as_chunk = TRUE, # using the "general" footnote option "Note." and the "Footnote...." text start on the same line
             threeparttable = TRUE,
             general = paste0("\\\\footnotesize{",footnote,"}"),
             escape =FALSE)
  )
}

# https://stackoverflow.com/questions/66472411/how-to-reduce-size-of-footnote-in-kableextra-latex




\begin{table}[H]
\centering
\fontsize{13pt}{20pt}\selectfont
\begin{tabular}{p{1cm} p{14cm}}
\hline
\textbf{K} & \textbf{$\boldsymbol \sigma$} \\
\hline
\hline
10 & (0.14, 0.33, 0.15, 0.23, 0.07, 0.19, 0.19, 0.37, 0.32, 0.11)$'$ \\
\hline
20 & (0.14, 0.33, 0.15, 0.23, 0.07, 0.19, 0.19, 0.37, 0.32, 0.11, 0.17, 0.27, 0.24, 0.11, 0.11, 0.13, 0.16, 0.15, 0.15, 0.25)$'$ \\
\hline
30 & (0.14, 0.33, 0.15, 0.23, 0.07, 0.19, 0.19, 0.37, 0.32, 0.11, 0.17, 0.27, 0.24, 0.11, 0.11, 0.13, 0.16, 0.15, 0.15, 0.25, 0.15, 0.13, 0.1, 0.1, 0.24, 0.13, 0.32, 0.19, 0.27, 0.3)$'$ \\
\hline
40 & (0.14, 0.33, 0.15, 0.23, 0.07, 0.19, 0.19, 0.37, 0.32, 0.11, 0.17, 0.27, 0.24, 0.11, 0.11, 0.13, 0.16, 0.15, 0.15, 0.25, 0.15, 0.13, 0.1, 0.1, 0.24, 0.13, 0.32, 0.19, 0.27, 0.3, 0.12, 0.27, 0.09, 0.12, 0.36, 0.09, 0.15, 0.16, 0.09, 0.29)$'$ \\
\hline
50 & (0.14, 0.33, 0.15, 0.23, 0.07, 0.19, 0.19, 0.37, 0.32, 0.11, 0.17, 0.27, 0.24, 0.11, 0.11, 0.13, 0.16, 0.15, 0.15, 0.25, 0.15, 0.13, 0.1, 0.1, 0.24, 0.13, 0.32, 0.19, 0.27, 0.3, 0.12, 0.27, 0.09, 0.12, 0.36, 0.09, 0.15, 0.16, 0.09, 0.29, 0.16, 0.28, 0.14, 0.07, 0.2, 0.31, 0.13, 0.14, 0.31, 0.11)$'$ \\
\hline
\end{tabular}
\end{table}




```{r}
# tabb1 <- preprocess_tightness_measure(eq_res, "t2", equicorr, TRUE)
# 
# if (!equicorr) {
#   tabb1 <- tabb1 %>% select(-c(r, blocks))
# }
# 
# tabb1 <- tabb1 %>% select(K, r,
#     independent_low, bonferroni_low, nonrankbased_low,
#     independent_med, bonferroni_med, nonrankbased_med,
#     independent_high, bonferroni_high, nonrankbased_high,
#     rankbased_asymptotic_low, rankbased_level2bs_low,
#     rankbased_asymptotic_med, rankbased_level2bs_med,
#     rankbased_asymptotic_high, rankbased_level2bs_high)
# create_table_for_tightness_measure(
#   summary=tabb1,
#   metric_type="$T_2$",
#   equicorr)
```

```{r}
# tabb1 <- preprocess_tightness_measure(eq_res, "t2", equicorr, TRUE)
# 
# if (!equicorr) {
#   tabb1 <- tabb1 %>% select(-c(r, blocks))
# }
# 
# tabb1 <- tabb1 %>% select(K, r,
#     independent_low, bonferroni_low, nonrankbased_low,
#     independent_med, bonferroni_med, nonrankbased_med,
#     independent_high, bonferroni_high, nonrankbased_high,
#     rankbased_asymptotic_low, rankbased_level2bs_low,
#     rankbased_asymptotic_med, rankbased_level2bs_med,
#     rankbased_asymptotic_high, rankbased_level2bs_high)
# create_table_for_tightness_measure(
#   summary=tabb1,
#   metric_type="$T_3$",
#   equicorr)
```


```{r include = FALSE}
# tabb <- preprocess_tightness_measure(combined, "t1", equicorr, FALSE)
# 
# if (!equicorr) {
#   tabb <- tabb %>% select(-c(r, blocks))
# }

# create_table_for_tightness_measure(
#   summary=tabb,
#   metric_type="T1", equicorr, FALSE)
```

```{r include = FALSE}
# tabb <- preprocess_tightness_measure(combined, "t2", equicorr, FALSE)
# 
# if (!equicorr) {
#   tabb <- tabb %>% select(-c(r, blocks))
# }


# create_table_for_tightness_measure(
#   summary=tabb, 
#   metric_type="T2", equicorr, FALSE)
```

```{r include = FALSE}
# tabb <- preprocess_tightness_measure(combined, "t3", equicorr, FALSE)
# 
# if (!equicorr) {
#   tabb <- tabb %>% select(-c(r, blocks))
# }

# create_table_for_tightness_measure(
#   summary=tabb, 
#   metric_type="T3", equicorr, FALSE)
```


\elandscape


```{r simulation-table1, results='asis', include=FALSE}
library(dplyr)
library(tidyr)
mean <- 23.8
sds <-c('low', 'medium', 'high')# c(2, 3.6, 6)
Ks <- c(10, 20, 30, 40, 50)
#corrs <- c(0.1,0.5,0.9)
alphas <- c(0.05)#c(0.05, 0.1, 0.15, 0.2)

theta <- c()
std <- c()
K <- c()
i <-1   # initialize index

for (k in Ks) {
  for (sd in sds) {

    set.seed(123974)
    true_theta <- sd #rnorm(k, mean, sd)
    value_to_add <- true_theta#paste(round(true_theta,1), collapse = ", ")
    theta[i] <- value_to_add
    std[i] <- sd
    K[i] <- k
    i <- i + 1
  }
}

reals <- data.frame(theta, K, std)


# grid <- grid %>%

# grid#dplyr::inner_join(grid, reals, by = c("std", "K"))

reals <- data.frame(theta, K, std)

K <- c(10, 20, 30, 40, 50)
sd <-c(2.0, 3.6, 6.0)# my_list
R_type <- c("R_eq", "R_block")

reals$R <- rep(list(R_type), nrow(reals))
table_to_plot <- reals %>%
  unnest(R) %>%
  mutate(
    `$\\mathbf{R}$` = case_when(
      R == "R_eq" ~ "$\\mathbf{R}_{\\text{eq}}, \\rho = 0.1, 0.5, 0.9$",
      R == "R_block" ~ "$\\mathbf{R}_{\\text{block}} \\text{(2 or 3 blocks)}$"
    )
  ) %>%
  select(theta, `$\\mathbf{R}$`, K)
```

```{r asis = TRUE, include = FALSE}
library(kableExtra)


kable(table_to_plot, "latex", booktabs = TRUE, escape = FALSE,linesep = "",
      longtable = TRUE) %>%
  column_spec(1, width = "10cm") %>%    # wrap column 1
  column_spec(2, width = "5cm") %>%
  kable_styling(
    latex_options = c("striped", "repeat_header", "HOLD_position"),
    stripe_color = "gray!15"  # light gray, can change
  )
```

```{r simulation-table, results='asis', include=FALSE}
library(dplyr)
library(tidyr)
mean <- 23.8
sds <- c(2, 3.6, 6)
Ks <- c(10, 20, 30, 40, 50)
#corrs <- c(0.1,0.5,0.9)
alphas <- c(0.05)#c(0.05, 0.1, 0.15, 0.2)

theta <- c()
std <- c()
K <- c()
i <- 1   # initialize index

for (k in Ks) {
  for (sd in sds) {

    set.seed(123974)
    true_theta <- rnorm(k, mean, sd)
    value_to_add <- paste(round(true_theta,1), collapse = ", ")
    theta[i] <- value_to_add
    std[i] <- sd
    K[i] <- k
    i <- i + 1
  }
}

reals <- data.frame(theta, K, std)


# grid <- grid %>%

# grid#dplyr::inner_join(grid, reals, by = c("std", "K"))

reals <- data.frame(theta, K, std)

K <- c(10, 20, 30, 40, 50)
sd <-c(2.0, 3.6, 6.0)# my_list
R_type <- c("R_eq", "R_block")

reals$R <- rep(list(R_type), nrow(reals))
table_to_plot <- reals %>%
  unnest(R) %>%
  mutate(
    `$\\mathbf{R}$` = case_when(
      R == "R_eq" ~ "$\\mathbf{R}_{\\text{eq}}, \\rho = 0.1, 0.5, 0.9$",
      R == "R_block" ~ "$\\mathbf{R}_{\\text{block}} \\text{(2 or 3 blocks)}$"
    )
  ) %>%
  select(theta, `$\\mathbf{R}$`)
```

```{r asis = TRUE, include = FALSE}
library(kableExtra)


kable(table_to_plot, "latex", booktabs = TRUE, escape = FALSE,linesep = "",
      longtable = TRUE) %>%
  column_spec(1, width = "10cm") %>%    # wrap column 1
  column_spec(2, width = "5cm") %>%
  kable_styling(
    latex_options = c("striped", "repeat_header", "HOLD_position"),
    stripe_color = "gray!15"  # light gray, can change
  )
```

```{r, results='asis', echo=FALSE, warning=FALSE, include=FALSE}
code <- readLines("../../R/simulate/compute_ci.R")
cat("```r\n", paste(code, collapse = "\n"), "\n```")
```

```{r, results='asis', echo=FALSE, warning=FALSE, include=FALSE}
code <- readLines("../../R/simulate/compute_metrics.R")
cat("```r\n", paste(code, collapse = "\n"), "\n```")
```


```{r, results='asis', echo=FALSE, warning=FALSE, include=FALSE}
code <- readLines("../../R/simulate/implement.R")
cat("```r\n", paste(code, collapse = "\n"), "\n```")
```





# prepare_t_facet_plot_data(
#     eq_data = eq_res,
#     bl_data = bl_res,
#     unordered = FALSE) %>%
#   mutate(Variability = factor(Variability,
#                               levels = c("low", "med", "high"),
#                               labels = c("Low", "Moderate", "High"),
#                               ordered = TRUE),
#          #================================
#          Approach = factor(Approach,
#                            levels = c("rankbased_asymptotic","rankbased_level2bs"),
#                            labels = c("asymptotic", "level2bs"),
#                            ordered = TRUE),
#          #================================
#          `Correlation structure` = factor(`Correlation structure`,
#                                           levels =c("Equicorrelated", "Block diagonal"),
#                                           labels =c("Equicorr", "Block diag")),
#          K = factor(K,
#                     levels = c('10','20','30','40',"50"),
#                               labels = paste("K =",c('10','20','30','40',"50")),
#                               ordered = TRUE),
#          Metric = factor(Metric,
#                          levels = c('t1', 't2', 't3'),
#                          labels = c("T[1]", "T[2]", "T[3]"),
#                          ordered = TRUE)) %>%
#   ggplot(aes(x = `Correlation structure`,
#              y = Values, 
#              color = factor(r),
#              #linetype = `Correlation structure`,
#              shape = Variability,
#              group = interaction(Variability,r))) +
#   geom_point(alpha = 0.75) +# geom_line(color = 'black', size = 0.05) +
#   # facet_grid(Metric ~ K ,scales = "free") +
#   facet_grid(Approach + Metric ~ K ,scales = "free",
#             labeller = labeller(
#                Metric = label_parsed, # Interprets "T[1]" as math
#                #K = label_value        # Keeps "K = 10" as literal text
#              )) +
#              # labeller = labeller(`Correlation structure` = function(x) rep("", length(x)))) +
# 
# 
#     #labs(title=title) + xlab(xlab) + ylab(ylab) +
#     theme_bw() +
#   # labs(title="") +
#     theme(axis.text.x = element_text(hjust = 1, size = 7, angle = 45),
#           axis.text.y = element_text(size=7)
#           # strip.background.y = element_blank()
#     ) +
#     guides(color = guide_legend(title = "r", ncol = 7)) +
#     theme(axis.line = element_line(colour = "gray"),
#           panel.grid.minor = element_blank(),
#           panel.grid.major.x = element_blank(),
#           text = element_text(family = "serif"),
#           legend.position = "top",
#           legend.box = "vertical",
#           legend.spacing.y = unit(0.05, "cm"),
#           legend.box.just = "left",
#           legend.margin = margin(t=.15, b=0.15,l=0.5, r=0.5, "cm"),
#           legend.background = element_blank(), # Make individual legend backgrounds transparent
#           legend.box.background = element_rect(colour = "black") # Add a single box around all legends
#           # legend.box.margin = margin(1, 1, 1, 1, "mm"),
# 
#           # aspect.ratio = 1
#           # Add some margin
#     ) #+ coord_flip()




# create_table_for_coverage <- function(summary, footnote, equicorrelation = TRUE,
#                                       unordered = TRUE){
#   
#   if (equicorrelation) {
#     vector_1 <- c("K", "r")
#     striped <- rep(c(0, 6, 12), each = 3) + 1:3
#   } else {
#     vector_1 <- c("K")
#     striped <- -1
#   }
#   
#   if (unordered) {
#     selected_columns <- c("Independent","Bonferroni","Nonrank")
#     colwidth  <- "3cm"
#   } else {
#     selected_columns <- c("Asymptotic Variance","Bootstrap Estimate")
#     colwidth  <- "4cm"
#   }
#   num <- length(selected_columns)
#   formatted <- summary %>%
#     kable("latex",
#           booktabs = TRUE,
#           escape = FALSE,
#           linesep = "",
#           longtable = TRUE,
#           align = "c",
#           col.names = c(vector_1,
#                         selected_columns),
#           caption = "Simulation Results for Coverage Probabilities")
# 
#   if (equicorrelation) {
#     final <- formatted %>% 
#       column_spec(1:2, width = "1cm") %>%
#       column_spec(3:(2+num), width = colwidth)
#   } else {
#     final <- formatted %>% 
#       column_spec(1:1, width = "1cm") %>%
#       column_spec(2:(1+num), width = colwidth) %>%
#       pack_rows("2 balanced blocks", 1, 5) %>%
#       pack_rows("2 unbalanced blocks", 6, 10) %>%
#       pack_rows("3 unbalanced blocks - low", 11, 15) %>%
#       pack_rows("3 unbalanced block - high", 16, 20) 
#   }
#   
#   return(
#     final %>% 
#       collapse_rows(columns = 1,
#                     valign = "middle", 
#                     latex_hline = "none",
#                     row_group_label_position = "first") %>%
#       kable_styling(latex_options = c("striped", 
#                                       "repeat_header", 
#                                       "HOLD_position"),
#                     stripe_color = "gray!15",
#                     stripe_index = striped,
#                     font_size=FONT_SIZE) %>%
#     footnote(general_title = "\\\\footnotesize\\\\textit{Note: }", 
#              footnote_as_chunk = TRUE, # using the "general" footnote option "Note." and the "Footnote...." text start on the same line
#              threeparttable = TRUE,
#              general = paste0("\\\\footnotesize{",footnote,"}"),
#              escape =FALSE)
#   )
# }


# preprocess_tightness_measure <- function(dataset, metric_type, equicorrelation){
#   if (equicorrelation) {
#     vector1 <- c('K', 'r')
#   } else {
#     vector1 <- c('K', 'r', 'blocks')
#   }
#   
#   levels <- c('low', 'med', "high")
#   # if (unordered) {
#   #   selected_columns <- c('independent', 'bonferroni', 'nonrankbased')
#   # } else {
#   #   selected_columns <- c('rankbased_asymptotic', 'rankbased_level2bs')
#   # }
#   selected_columns <- c('independent', 'bonferroni', 'nonrankbased',
#                         'rankbased_asymptotic', 'rankbased_level2bs')
#   
#   return(
#     dataset %>%
#       mutate(across(c(selected_columns), round, 3)) %>% 
#       filter(metric == metric_type) %>% 
#       mutate(Variance = ifelse(sd==2.0, 
#                                   'low', 
#                                   ifelse(sd == 3.6, 'med', 'high'))) %>%
#       select(
#         c(vector1, c(Variance, selected_columns)
#         )
#       ) %>%
#       tidyr::pivot_wider(names_from = Variance, 
#                          values_from = selected_columns, 
#                          names_sep = "_") %>%
#       select(
#         c(vector1, unlist(lapply(levels, 
#                                  function(x) {paste(selected_columns, 
#                                                     x, 
#                                                     sep = '_')}))
#         )
#       )
#   )
# } 
