---
title: "Beamer from RMarkdown"
subtitle: "A repreducible example"
author: "Matala, Shaine"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
institute: "University of the Philippines"
fontsize: 9pt
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "beaver"
    fonttheme: "structurebold"
    incremental: false
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Two column layout


\begin{columns}
\column{0.50\textwidth}

```{r out.width="100%"}
hist(rnorm(1000,0,1))
```


\column{0.50\textwidth}
This is a normal distribution.In Figure 2.2, the x-axis represents the distribution of possible
batting averages, and the y-axis represents the probability density
of the beta distribution: how likely the batting average is to fall at a
particular point. The beta distribution is representing a probability
distribution of probabilities.
Here’s why the beta distribution is so appropriate for modeling
the binomial. Imagine the player gets a single hit. His record for
the season is now “1 hit; 1 at bat.” We have to then update our
probabilities- we want to shift this entire curve over just a bit to
reflect our new information. This is the Bayesian philosophy in a
nutshell: we start with a prior distribution, see some evidence, then
update to a posterior distribution.
The math for proving this is a bit involved (it’s shown here), the
result is very simple. The new beta distribution will be:
\end{columns}


# Code blocks

\begin{alertblock}{Alert block}
$$
E = mc^2
$$
\end{alertblock}

\begin{examples}
Example blocks are automatically green in color
\end{examples}

### Blue block

- happens with level 2, 3 headings
- this is only true for 'Madrid' theme in R Markdown!!


# This works, incremental bullets

>- Bullet 1
>- Bullet 2

# This nests, but does not increment

- Bullet 1
- Bullet 2
    + subbullet 1
    + subbullet 2

# This increments

>- Bullet 1
>- Bullet 2
>    - subbullet 1
>    - subbullet 2

# This increments too

>- Bullet 1
>- Bullet 2
>    + subbullet 1
>    + subbullet 2


# Text

Today is going to be a great day

## Today is...

A new beginning.

## Your Reference

- [slideshare](https://www.slideshare.net/slideshow/create-beamer-slide-with-r-markdown/105158435)
- [themes](https://mpetroff.net/files/beamer-theme-matrix/)
- [incremental bullets](https://stackoverflow.com/questions/49367078/incremental-sub-bullets-in-rmarkdown-and-beamer)