---
number_sections: true
fig_caption: yes
output:
  bookdown::pdf_document2:
    toc: false
fontsize: 12pt 
indent: true
header-includes:
- \usepackage{amsmath}
- \numberwithin{equation}{section}
- \usepackage{setspace}\doublespacing
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{indentfirst}
- \usepackage{xparse}
papersize: a4
bibliography: /home/realiseshewon/PDev/kde-ranking/writeup/references.bib
csl: /home/realiseshewon/PDev/kde-ranking/writeup/harvard-educational-review.csl
---



\title{\vspace{20mm}TITLE HERE}
\maketitle
\thispagestyle{empty} 
\vspace*{95px}
\begin{center}
A Thesis Proposal Presented to\\
The Faculty of the SS\\
univ\\
\vspace*{100px}
In Partial Fulfillment\\
of the Requirements for the Degree of\\
degree\\
1st Semester A.Y. 2025-2026

\vspace*{100px}
by\\
Nmae
\end{center}


\newpage


# Abstract {-}



```{r, child = "child/abstract.Rmd"}

```

\newpage

\tableofcontents

\newpage

# Introduction

```{r, child = "child/introduction.Rmd"}

```

# Literature Review

```{r, child = "child/rrl.Rmd"}

```

# Methodology

```{r, child = "child/methodology.Rmd"}

```

THIS IS @mariarizzo

# References


# Appendices {-}

```{r, child = "child/appendix.Rmd"}

```

