---
number_sections: true
fig_caption: yes
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
    highlight: kate # monochrome
indent: true
header-includes:
- \usepackage{amsmath}
- \numberwithin{equation}{section}
- \usepackage{setspace}\onehalfspacing
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{indentfirst}
- \usepackage{xparse}
- \usepackage{algorithm}
- \usepackage{algpseudocode}
- \usepackage{float}
- \usepackage{placeins}
- \renewcommand{\ttfamily}{\rmfamily}
- \usepackage{etoolbox}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{booktabs}
- \AtBeginEnvironment{algorithmic}{\setstretch{1.5}} 
- \renewcommand{\arraystretch}{0.75}
- \renewcommand{\multirowsetup}{\raggedright}
# --- Thesis font definition (change here once, affects everything) ---
- \usepackage{anyfontsize}
- \newcommand{\thesisfont}{\fontsize{20pt}{19pt}\selectfont}
- \thesisfont

# --- Section headers proportional to body font ---
- \usepackage{titlesec}
- \titleformat{\section}{\fontsize{20pt}{22pt}\bfseries}{\thesection}{1em}{}
- \titleformat{\subsection}{\fontsize{18pt}{20pt}\bfseries}{\thesubsection}{1em}{}
- \titleformat{\subsubsection}{\fontsize{16pt}{19pt}\bfseries}{\thesubsubsection}{1em}{}

# --- Algorithms (caption + body + pseudocode) ---
- \usepackage{caption}
- \newcommand{\algfont}{\fontsize{15pt}{18pt}\selectfont}   # slightly smaller than thesis font
- \DeclareCaptionFont{thesisalg}{\algfont\bfseries}         # caption font
- \captionsetup[algorithm]{font=thesisalg}
- \AtBeginEnvironment{algorithm}{\algfont}                  # algorithm body
- \AtBeginEnvironment{algorithmic}{\algfont}   

papersize: a4
bibliography: /home/realiseshewon/PDev/kde-ranking/writeup/references.bib
nocite: | 
  @elias
  @wright
  @sidak
  @dunn
  @pork
  @healy
csl: /home/realiseshewon/PDev/kde-ranking/writeup/harvard-educational-review.csl
---
\fontsize{15pt}{18pt}\selectfont

\title{%
  \vspace{35mm}% <- reduce this from 45mm to something smaller
  \textbf{Joint Confidence Regions for Rankings based on Correlated Estimates}%
}
\maketitle
\thispagestyle{empty}
\begin{center}
Shaine Rosewel Paralis Matala\\
\vspace*{32px}
A Thesis proposal submitted to UP Diliman School of Statistics\\
\vspace*{14px}
In Partial Fulfillment of the Requirements for the Degree of\\
Master of Science in Statistics\\
\vspace*{250px}
School of Statistics\\
University of the Philippines\\
November 2025
\end{center}

\newpage

```{r echo = FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE
)
```

\newpage

\tableofcontents
\newpage
\vspace*{1cm}

# Introduction

\vspace*{0.8cm}

```{r, child = "child/introduction.Rmd", echo = FALSE}

```

\newpage
\vspace*{1cm}

# Related Literature

\vspace*{0.8cm}

```{r, child = "child/rrl.Rmd", echo = FALSE}

```

\newpage
\vspace*{1cm}

# Methodology

\vspace*{0.8cm}

```{r, child = "child/methodology.Rmd"}

```

\newpage
\vspace*{1cm}

# Bibliography {.unnumbered .unnumbered .unlisted}

\vspace*{0.8cm}

::: {#refs}
:::
