---
number_sections: true
fig_caption: yes
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
    highlight: kate # monochrome
fontsize: 12pt 
indent: true
header-includes:
- \usepackage{amsmath}
- \numberwithin{equation}{section}
- \usepackage{setspace}\onehalfspacing
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{indentfirst}
- \usepackage{xparse}
- \usepackage{algorithm}
- \usepackage{algpseudocode}
- \usepackage{float}
- \usepackage{placeins}
- \renewcommand{\ttfamily}{\rmfamily}
- \usepackage{etoolbox}
- \AtBeginEnvironment{algorithmic}{\setstretch{1.5}} 
- \renewcommand{\arraystretch}{0.75}                  

papersize: a4
bibliography: /home/realiseshewon/PDev/kde-ranking/writeup/references.bib
nocite: | 
  @elias
csl: /home/realiseshewon/PDev/kde-ranking/writeup/harvard-educational-review.csl
---

\title{%
  \vspace{35mm}% <- reduce this from 45mm to something smaller
  \textbf{Joint Confidence Regions for Rankings based on Correlated Estimates}%
}
\maketitle
\thispagestyle{empty}
\begin{center}
Shaine Rosewel Paralis Matala\\
\vspace*{32px}
A Thesis proposal submitted to UP Diliman School of Statistics\\
\vspace*{14px}
In Partial Fulfillment of the Requirements for the Degree of\\
Master of Science in Statistics\\
\vspace*{280px}
School of Statistics\\
University of the Philippines\\
November 2025
\end{center}


\newpage


```{r echo = FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE
)
```

\newpage

\tableofcontents
\newpage
\vspace*{1cm}

# Introduction
\vspace*{0.8cm}

```{r, child = "child/introduction.Rmd", echo = FALSE}

```

\newpage
\vspace*{1cm}

# Related Literature
\vspace*{0.8cm}

```{r, child = "child/rrl.Rmd", echo = FALSE}

```

\newpage
\vspace*{1cm}

# Methodology
\vspace*{0.8cm}

```{r, child = "child/methodology.Rmd"}

```


\newpage
\vspace*{1cm}
# Bibliography {- .unnumbered .unlisted}
\vspace*{0.8cm}
<div id="refs"></div>

