---
number_sections: true
fig_caption: yes
output:
  bookdown::pdf_document2:
    toc: false
    highlight: kate # monochrome
fontsize: 12pt 
indent: true
header-includes:
- \usepackage{amsmath}
- \numberwithin{equation}{section}
- \usepackage{setspace}\onehalfspacing
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{indentfirst}
- \usepackage{xparse}
- \usepackage{algorithm}
- \usepackage{algpseudocode}
- \usepackage{float}
- \renewcommand{\ttfamily}{\rmfamily}
papersize: a4
bibliography: /home/realiseshewon/PDev/kde-ranking/writeup/references.bib
csl: /home/realiseshewon/PDev/kde-ranking/writeup/harvard-educational-review.csl
---



\title{\vspace{20mm}TITLE HERE}
\maketitle
\thispagestyle{empty} 
\vspace*{95px}
\begin{center}
Shaine Rosewel Paralis Matala\\
\vspace*{85px}
A Thesis proposal submitted to UP Diliman School of Statistics\\
\vspace*{15px}
In Partial Fulfillment of the Requirements for the Degree of\\
Master of Science in Statistics\\
\vspace*{200px}
School of Statistics\\
University of the Philippines\\
Month Year
\end{center}


\newpage


```{r echo = FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE
)
```

\newpage

\tableofcontents

\newpage

# Introduction

```{r, child = "child/introduction.Rmd", echo = FALSE}

```


# Related Literature


```{r, child = "child/rrl.Rmd", echo = FALSE}

```


# Methodology

```{r, child = "child/methodology.Rmd"}

```



# Bibliography {- .unnumbered .unlisted}
<div id="refs"></div>

