The outcomes of the simulation studies are organized into Sections \ref{sec:unordered-results} and \ref{sec:ordered-results} for the unordered and ordered parameters, respectively.

## Joint Confidence Region for the Unordered Parameters {#sec:unordered-results}

The resulting joint confidence regions for the unordered parameters obtained through the proposed Algorithm \ref{alg:nonrank_ci} (`r NONRANK$SHORTNAME`) are compared to those from Klein's independent assumption and Bonferroni approaches, which we will refer to as `r IND$SHORTNAME` and `r BONF$SHORTNAME`. This is to show the advantage of using the proposed algorithm in the presence of correlation among ranked estimates. 

Figure \ref{fig:nonrank-cov-plot} plots $K$ against the difference between the observed coverage and the nominal level of 0.95. Ideally, these values should be close to 0, indicating that the coverage is near the nominal level. Values much greater than 0 indicate conservative joint confidence regions, whereas values much less than zero indicate anti-conservative behavior.

The first row of Figure \ref{fig:nonrank-cov-plot} shows results for an assumed equicorrelated structure. 

Its first two facets illustrate that the difference between the coverage and 0.95 tends to be greater than zero for both `r IND$SHORTNAME` and `r BONF$SHORTNAME` with moderate to high $\rho$, irrespective of $K$. In some cases, coverage reaches approximately 0.99 when the correlation is high ($\rho = 0.9$) and the number of estimates is large (e.g., $K = 50$). In contrast, `r NONRANK$SHORTNAME`, shown in the third facet, consistently produces coverage within 0.01 of the nominal level, regardless of $\rho$. The advantage of Algorithm \ref{alg:nonrank_ci} is therefore evident at moderate to high levels of correlation.

For the block diagonal correlation structures shown in the second row of Figure \ref{fig:nonrank-cov-plot}, the improvement from Algorithm \ref{alg:nonrank_ci} becomes distinguishable when larger block sizes have higher $\rho$. This is particularly evident for B2 and UH3 where 50% of the estimates are highly correlated. In U2, 30% of the estimates are highly correlated, while in UL3, only 20% are highly correlated. Under milder correlation setups such as U2 and UL3, `r NONRANK$SHORTNAME` has little to no advantage over  `r IND$SHORTNAME` and `r BONF$SHORTNAME`.

The improvement from Algorithm \ref{alg:nonrank_ci} is diminished for the block diagonal correlation structure compared to that of the equicorrelation structure. This is because the correlation among estimates is weaker in the block diagonal structure, where off-diagonal blocks are zero. Moreover, since `r IND$SHORTNAME` and `r BONF$SHORTNAME` become increasingly conservative as $K$ increases and as more estimates become moderately to highly correlated, the proposed algorithm is expected to provide closer to nominal coverage in such settings.

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
source("/home/realiseshewon/PDev/kde-ranking/R/preprocess_data.R")
source("/home/realiseshewon/PDev/kde-ranking/R/create_table.R")
source("/home/realiseshewon/PDev/kde-ranking/R/create_plot.R")
source("/home/realiseshewon/PDev/kde-ranking/R/CONSTANTS.R")


eq_res <- combine_summaries(
  "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_k",
  TRUE
) %>% mutate(
  Variance = factor(ifelse(sd == 2, LOW$NAME,
                           ifelse(sd == 3.6, MED$NAME, HIGH$NAME)),
                    levels = c(LOW$NAME, MED$NAME, HIGH$NAME), 
                    ordered = TRUE)) %>% 
  mutate(`Correlation structure` = EQUICORRELATED$NAME) %>%
  mutate(across(c(nonrankbased, rankbased_asymptotic, rankbased_level2bs, 
                  independent, bonferroni), round, 3)) 
  #mutate(across(5:8, round, 3))


bl_res <- combine_summaries(
  "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_block",
  FALSE
) %>% 
mutate(
  Variance = factor(ifelse(sd == 2, 'Low', 
                    ifelse(sd == 3.6, "Moderate", "High")),
                    levels = c("Low", "Moderate", "High"), 
                    ordered = TRUE),
  
  r = factor(
    case_when(
      r == "balanced-block" & blocks == 2 ~ "B2",
      r == "unbalanced-block" & blocks == 2 ~ "U2",
      r == "unbalanced-block" & blocks == 3 ~ "UL3",
      r == "unbalanced-block-high" & blocks == 3 ~ "UH3",
      TRUE ~ r
    ),
    levels = c("B2", "U2", "UL3", "UH3"),
    ordered = TRUE
  )
) %>% 
    mutate(`Correlation structure` = "Block Diagonal") %>%
  mutate(across(c(nonrankbased,rankbased_asymptotic, rankbased_level2bs, independent, bonferroni), round, 3)) 
```


```{r nonrank-cov-plot, fig.cap = "Simulation Result for Coverage of Unordered Parameters"}
forplot <- prepare_coverage_data_plot(eq_res, bl_res, unordered = TRUE)
create_plot_for_coverage(forplot, unordered=TRUE)
```

The same coverage values are observed for different variance levels of the true parameters, $V(\theta_k)$. This results from assuming the same known $\Sigma$ across cases. In Equation (\ref{eq:prb}), it follows that the distribution of $t$ depends only on $\Sigma$ and $K$. This is more intuitive in the bootstrap setting as demonstrated in Algorithm \ref{alg:nonrank_ci}. In step 2, we generate $\hat {\boldsymbol \theta}^*_b \sim N_K (\hat{\boldsymbol \theta}, \Sigma)$ and compute $\underset{k}{\max} \left| \frac{\hat{\theta}_{bk}^* - \hat{\theta}_k}{\sigma_k} \right|$ where $\hat{\boldsymbol \theta}_{b}^* - \hat{\boldsymbol \theta} \sim N_K(0, \Sigma)$. From Equation (\ref{eq:sigma_matrix}), this also implies that the correlation matrix $\mathbf{R}$ influences the coverage. 

Results for $T_1$, $T_2$, and $T_3$ tightness measures are shown in Figure \ref{fig:nonrank-plot}. The maximum possible value of  `r T3$MATHNAME` for each $K$ is denoted with the red dashed line. We want to observe lower values for both $T_1$ and $T_2$ and higher ones for $T_3$. Altogether, these indicate that a method yields a tighter confidence region which implies less overall uncertainty.

For $\mathbf{R}_{\text{eq}}$, shown in rows 1 to 3 of Figure \ref{fig:nonrank-plot}, `r T1$MATHNAME`, `r T2$MATHNAME`, and `r T3$MATHNAME` values indicate that Algorithm \ref{alg:nonrank_ci} produces tighter confidence region than both `r IND$SHORTNAME` and `r BONF$SHORTNAME` when $\rho$ is moderate to high. In each facet, this is captured by the steepness of the line segments connecting the points, particularly  from `r BONF$SHORTNAME` to `r NONRANK$SHORTNAME`. It tends to be steeper when $\rho$ is higher. Given the same $K$ and correlation structure, the steepness of the slope also shows that the improvement in `r T1$MATHNAME`, `r T2$MATHNAME`, and `r T3$MATHNAME` is larger with lower variance in the parameters; this is easier to observe when $\rho = 0.9$ and $K=50$. When $\hat{\theta}$ values are more dispersed, the confidence region is narrower; however, as they vary less or become closer to each other, ranks tend to interchange more, resulting in a wider region. Hence, more room for improvement. 

Moreover, while regions become less tight with higher $K$, as shown by the groupwise upward movement of the points from the left to the right facet for rows 1 and 2 of Figure \ref{fig:nonrank-plot}, the increase in `r T1$MATHNAME` and `r T2$MATHNAME` is larger for parameters that vary less. This is demonstrated by the corresponding jumps of each group of same-size points across facets. As we rank more estimates, our uncertainty increases at a higher rate when the corresponding parameters are close to each other than when they are widely separated. Meanwhile, `r T3$MATHNAME` is less sensitive to $K$ than `r T1$MATHNAME` and `r T2$MATHNAME` since it divides $OP$ by $K^2$ as defined in Equation \ref{eq:t3}. 

```{r nonrank-plot,fig.pos = "!htbp", fig.cap = "Simulation Result for Tightness Measure of Unordered Parameters", fig.height=8.75}
create_plot_for_t(prepare_t_facet_plot_data(
    eq_data = eq_res,
    bl_data = bl_res,
    unordered = TRUE), unordered = TRUE)
```

The last three rows of Figure \ref{fig:nonrank-plot} show the results for a block diagonal correlation structure. Similar to the coverage results, the overall benefit of using the `r NONRANK$SHORTNAME` is reduced compared to when an equicorrelated structure is enforced. In each facet, this is illustrated through flatter slopes of line segments connecting the points corresponding to `r BONF$SHORTNAME` and the `r NONRANK$SHORTNAME`. Otherwise, the patterns observed for the equicorrelated structure remain consistent.

Overall, these trends show that the proposed approach is most advantageous in the presence of moderate to high correlation, especially when ranking a larger number of estimates whose underlying parameters have low variance.

The coverage values corresponding to Figure \ref{fig:nonrank-cov-plot} and the values for $T_1$, $T_2$ and $T_3$ in Figure \ref{fig:nonrank-plot} are provided in Tables \ref{tab:nonrank-eq-cov} and \ref{tab:nonrank-eq-t1}–\ref{tab:nonrank-eq-t3}, respectively, in the Appendix.

## Joint Confidence Region for the Ordered Parameters {#sec:ordered-results}

Figures \ref{fig:rank-cov-plot} and \ref{fig:rank-plot} are similar to plots introduced in the previous section but show joint confidence regions for the ordered parameters namely, `r ASYMP$SHORTNAME` and `r BOOT$SHORTNAME`. With confidence regions for ranks, we are not able to map the intervals to the estimates.

The first column of Figure \ref{fig:rank-cov-plot} illustrates how coverage for `r ASYMP$SHORTNAME` deviates from the nominal level. The deviation is almost always negative, indicating that `r ASYMP$SHORTNAME` is mostly anti-conservative. Undercoverage is largest when the parameters are widely spread, but the deviation is somewhat smaller for $K=50$. Under high $V(\theta)$, we can also observe that lower $K$ is associated with lower coverage for a given correlation. 

Some cases with intermediate $K$ (e.g., $K=20$ in row 4) show smaller deviation from nominal for B2, UL3, and UH3 compared to U2. To sum up, coverage can vary with no discernible pattern across correlations and $K$ except when $V(\theta)$ is high.

The second column of Figure \ref{fig:rank-cov-plot} presents coverage for `r BOOT$SHORTNAME`. It produces coverage values that do not deviate systematically from and are relatively closer to nominal when compared to `r ASYMP$SHORTNAME`. With the two proposed approaches, it is clear that `r BOOT$SHORTNAME` is superior to `r ASYMP$SHORTNAME` in terms of coverage.

```{r rank-cov-plot, fig.cap = "Simulation Result for Coverage of Ordered Parameters", fig.height = 7}
forplot <- prepare_coverage_data_plot(eq_res, bl_res, unordered = FALSE)
create_plot_for_coverage(forplot, unordered=FALSE)
```

Figure \ref{fig:rank-plot} shows the resulting `r T1$MATHNAME` for the joint confidence regions of ordered parameters. The first two columns in each facet is for `r ASYMP$SHORTNAME` while the last two is for `r BOOT$SHORTNAME`.  `r T2$MATHNAME` and `r T3$MATHNAME` are not included in the plot since they behave similarly to `r T1$MATHNAME`, except that the effect of $K$ is less on `r T3$MATHNAME`.

```{r rank-plot, fig.cap = "Simulation Result for Tightness Measure of Ordered Parameters", fig.height = 7}

prepared_data <- prepare_t_facet_plot_data(
    eq_data = eq_res,
    bl_data = bl_res,
    unordered = FALSE) %>% filter(Metric == "t1") #%>% filter(Variance == "High")
unordered <- FALSE

if (unordered) {
  app_levels = c(IND$RAWCHAR, BONF$RAWCHAR, NONRANK$RAWCHAR) 
  app_labels = c(IND$SHORTNAME, BONF$SHORTNAME, NONRANK$SHORTNAME)
  x = "Approach"
  label_parsedx <- function(x) x
  rot <- 90
  facet_str <- "`Correlation structure` + Metric ~ K"
} else {
  app_levels = c(ASYMP$RAWCHAR,BOOT$RAWCHAR)
  app_labels = c(ASYMP$SHORTNAME, BOOT$SHORTNAME)
  #x =  "Correlation structure"
  x = "Approach"
  #facet_str <- "Approach + Metric ~ K"
  facet_str <- "Variance ~ K"
  # label_parsedx <- function(x) parse(text = as.character(x))
  label_parsedx <- function(x) x
  rot <- 90
}

var_levels <- c(LOW$NAME, MED$NAME, HIGH$NAME)
var_labels <- c(TeX(LOW$GGNAME),
                TeX(MED$GGNAME),
                TeX(HIGH$GGNAME))
legend_labs <- c(TeX("$\\rho = 0.1$"),
                TeX("$\\rho = 0.5$"),
                TeX("$\\rho = 0.9$"),
                #"B2", "U2", "UL3", "UH3")
                "UL3", "U2", "B2", "UH3")




dat <- prepared_data %>%
  mutate(
    `Correlation structure` = factor(`Correlation structure`,
                                     levels =c(EQUICORRELATED$NAME, 
                                               BLOCK_DIAGONAL$NAME),
                                     labels = c(TeX(EQUICORRELATED$GGNAME), 
                                                TeX(BLOCK_DIAGONAL$GGNAME))),
    r = ifelse(r == 0.1, "$\\rho = 0.1$", 
               ifelse(r == 0.5, "$\\rho = 0.5$", 
                      ifelse(r == 0.9,"$\\rho = 0.9$", r))),
    Approach = factor(Approach,
                      levels = app_levels, 
                      labels = app_labels,
                      ordered = TRUE),
    Variance = factor(Variance, 
                      levels = var_levels,
                      labels = var_labels,
                      ordered = TRUE),
    K = factor(K,
               levels = c('10','20','30','40',"50"),
               labels = paste("K =",c('10','20','30','40',"50")),
               #ordered = TRUE
               ),
    Metric = factor(Metric,
                    levels = c(T1$CHAR, T2$CHAR, T3$CHAR),
                    labels = c(TeX(T1$MATHNAME), 
                               TeX(T2$MATHNAME), 
                               TeX(T3$MATHNAME)),
                    #ordered = TRUE
                    )) %>%
  unite(col = "Correlation", 
        `Correlation structure`, 
        `r`, 
        sep = "_", 
        remove = FALSE)

  
corr_levels <- c(
  paste0(TeX(EQUICORRELATED$GGNAME), "_$\\rho = 0.1$"),
  paste0(TeX(EQUICORRELATED$GGNAME), "_$\\rho = 0.5$"),
  paste0(TeX(EQUICORRELATED$GGNAME), "_$\\rho = 0.9$"),
  paste0(TeX(BLOCK_DIAGONAL$GGNAME), "_UL3"),
  paste0(TeX(BLOCK_DIAGONAL$GGNAME), "_U2"),
  paste0(TeX(BLOCK_DIAGONAL$GGNAME), "_B2"),
  paste0(TeX(BLOCK_DIAGONAL$GGNAME), "_UH3")
)
dat$Correlation <- factor(dat$Correlation, levels = corr_levels)


t3_label <- labels(dat$Metric)[which(levels(dat$Metric) == TeX(T3$MATHNAME))]

maxt3 <- dat %>% 
  filter(Metric == levels(dat$Metric)[3]) %>% # Use index or exact label
  mutate(K_val = as.numeric(gsub("K = ", "", as.character(K))),
         max_t3 = (K_val - 1) / K_val) %>%
  distinct(Metric, K, max_t3)
  #===========================================================================


p <- dat %>%
  ggplot(aes(x = interaction(`Correlation structure`, Approach), # Combines both
             y = Values, 
             shape = Correlation, 
          #   size = Variance,
             fill = Correlation,
             group = interaction(`Correlation structure`,Approach) # Keeps groups distinct
             )) +
  geom_point(alpha = 0.3, stroke = 0.1) + 
  
  scale_size_ordinal(range = c(1, 2.25)) +
  scale_x_discrete(labels = label_parsedx) +
facet_grid(as.formula(facet_str),
           scales = "free",
           labeller = labeller(Metric = label_parsed,
                               `Correlation structure` = label_parsed,
                               Variance = label_parsed)) +
  geom_hline(data = maxt3, 
             aes(yintercept = max_t3),
             color = "red",
             linewidth = 0.25, 
             linetype = 'longdash')+

theme_bw() +
  theme(axis.text.x = element_text(#hjust = 1, 
                                   size = 9, angle = rot),
        axis.text.y = element_text(size=7)
  ) +
  scale_shape_manual(values =  c(21, 22, 23, 21, 22, 25, 24),
                     name = TeX(CORR_MATRIX$MATHNAME),
                     labels = legend_labs) +
  scale_fill_manual(name = TeX(CORR_MATRIX$MATHNAME),
                    labels = legend_labs,
                    values = c(rep("#B47846", 3),
                               rep("#4682B4", 4))) +
  scale_x_discrete(labels= c(TeX(paste(EQUICORRELATED$GGNAME, "Asymp")),
                             TeX(paste(BLOCK_DIAGONAL$GGNAME, "Asymp")), 
                             TeX(paste(EQUICORRELATED$GGNAME, "Boot")),
                             TeX(paste(BLOCK_DIAGONAL$GGNAME, "Boot")))) +
  COMMON_THEME +
  theme(axis.text.x = element_text(vjust = 0.5, hjust = 1, angle = 90)) +
  xlab("Correlation structure / Approach
       ")

if (unordered) {
  p <-p + geom_line(color = 'gray33', linewidth = 0.01)
}
p
```

Regions become wider with larger $K$ as shown by the upward, groupwise movement of points from left to right for `r T1$MATHNAME` in each row of Figure \ref{fig:rank-plot}. `r T1$MATHNAME` values are larger with lower $V(\theta)$. This is shown through the y-axis ranges for each row that corresponds to different a level of $V(\theta)$. Across different levels of $\rho$ in the equicorrelated structure, the difference in `r T1$MATHNAME` becomes more pronounced with larger $K$ and lower parameter variance. For the block correlation structure where correlation is generally weaker, these differences are less noticeable. These findings are all consistent with the outcomes for the unordered parameters.

Figure \ref{fig:rank-plot} shows that accounting for high correlation for `r BOOT$SHORTNAME` only helps tighten the joint confidence region when the parameters $\theta_1, \theta_2, \dots, \theta_K$ are well separated. This is easier to observe when considering the equicorrelated structure. When the parameters have a high $V(\theta)$, as shown in the third row of Figure \ref{fig:rank-plot}, it is evident that the `r BOOT$SHORTNAME` joint confidence region is lowest when $\rho = 0.9$. This remains true regardless of $K$. However, as $V(\theta)$ increases, higher $\rho$ tends to yield a wider region. This is the default behavior for `r ASYMP$SHORTNAME`. Furthermore, `r ASYMP$SHORTNAME` still produces regions that are wider than those of `r BOOT$SHORTNAME` even with its low coverage. These show that `r BOOT$SHORTNAME` is still more preferable than `r ASYMP$SHORTNAME` in terms of tightness measures.

The Appendix provides the coverage values for Figure \ref{fig:rank-cov-plot} (Table \ref{tab:rank-eq-cov}) and the values of `r T1$MATHNAME`, `r T2$MATHNAME`, and `r T3$MATHNAME` in Figure \ref{fig:rank-plot} (Tables \ref{tab:rank-eq-t1}–\ref{tab:rank-eq-t3}).

```{r rank-plot1, fig.cap = "Simulation Result for Tightness Measure of Ordered Parameters1", fig.height=8.75}
# create_plot_for_t(prepare_t_facet_plot_data(
#     eq_data = eq_res,
#     bl_data = bl_res,
#     unordered = FALSE), unordered = FALSE)
```



