The outcomes of the simulation studies are organized into Sections \ref{sec:unordered-results} and \ref{sec:ordered-results} for the unordered and ordered parameters, respectively.

## Joint confidence region for the unordered parameters {#sec:unordered-results}

The resulting joint confidence regions for the unordered parameters obtained through the proposed Algorithm \ref{alg:nonrank_ci} (`r NONRANK$SHORTNAME`) are compared to those from Klein's independent assumption and Bonferroni approaches, which we will refer to as `r IND$SHORTNAME` and `r BONF$SHORTNAME`. This is to show the advantage of using the proposed algorithm in the presence of correlation among ranked estimates. 

Figure \ref{fig:nonrank-cov-plot} plots $K$ against the difference between the observed coverage and the nominal level of 0.95. Ideally, these values should be close to 0, indicating that the coverage is near the nominal level. Values greater than 0 indicate conservative joint confidence regions, while values less than 0 indicate anti-conservative behavior.

The first row of Figure \ref{fig:nonrank-cov-plot} shows results for an assumed equicorrelated structure. Its first two facets illustrate that coverage values for both `r IND$SHORTNAME` and `r BONF$SHORTNAME` joint confidence regions tend to be greater than the nominal with moderate to high $\rho$, irrespective of $K$. In some cases, coverage reaches approximately 0.99 when the correlation is high ($\rho = 0.9$) and the number of estimates is large (e.g., $K = 50$). In contrast, `r NONRANK$SHORTNAME`, shown in the third facet, consistently produces coverage within 0.01 of the nominal level, regardless of $\rho$. The advantage of Algorithm \ref{alg:nonrank_ci} is therefore evident at moderate to high levels of correlation.

For the block diagonal correlation structures shown in the second row of Figure \ref{fig:nonrank-cov-plot}, the improvement from Algorithm \ref{alg:nonrank_ci} becomes distinguishable when larger block sizes have higher $\rho$. This is particularly evident for B2 and UH3 where 50% of the estimates are highly correlated. In U2, 30% of the estimates are highly correlated, while in UL3, only 20% are highly correlated. Under milder correlation setups such as U2 and UL3, `r NONRANK$SHORTNAME` has little to no advantage over  `r IND$SHORTNAME` and `r BONF$SHORTNAME`.

The improvement from Algorithm \ref{alg:nonrank_ci} is diminished for block diagonal correlation structure compared to that of equicorrelation structure. This is because the correlation among estimates is weaker in the block diagonal structure, where off-diagonal blocks are zero. Moreover, since `r IND$SHORTNAME` and `r BONF$SHORTNAME` become increasingly conservative as $K$ increases under moderate to high correlation, the proposed algorithm is expected to provide greater benefit in such settings.

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
source("/home/realiseshewon/PDev/kde-ranking/R/preprocess_data.R")
source("/home/realiseshewon/PDev/kde-ranking/R/create_table.R")
source("/home/realiseshewon/PDev/kde-ranking/R/create_plot.R")
source("/home/realiseshewon/PDev/kde-ranking/R/CONSTANTS.R")


eq_res <- combine_summaries(
  "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_k",
  TRUE
) %>% mutate(
  Variance = factor(ifelse(sd == 2, LOW$NAME,
                           ifelse(sd == 3.6, MED$NAME, HIGH$NAME)),
                    levels = c(LOW$NAME, MED$NAME, HIGH$NAME), 
                    ordered = TRUE)) %>% 
  mutate(`Correlation structure` = EQUICORRELATED$NAME) %>%
  mutate(across(c(nonrankbased, rankbased_asymptotic, rankbased_level2bs, 
                  independent, bonferroni), round, 3)) 
  #mutate(across(5:8, round, 3))


bl_res <- combine_summaries(
  "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_block",
  FALSE
) %>% 
mutate(
  Variance = factor(ifelse(sd == 2, 'Low', 
                    ifelse(sd == 3.6, "Moderate", "High")),
                    levels = c("Low", "Moderate", "High"), 
                    ordered = TRUE),
  
  r = factor(
    case_when(
      r == "balanced-block" & blocks == 2 ~ "B2",
      r == "unbalanced-block" & blocks == 2 ~ "U2",
      r == "unbalanced-block" & blocks == 3 ~ "UL3",
      r == "unbalanced-block-high" & blocks == 3 ~ "UH3",
      TRUE ~ r
    ),
    levels = c("B2", "U2", "UL3", "UH3"),
    ordered = TRUE
  )
) %>% 
    mutate(`Correlation structure` = "Block Diagonal") %>%
  mutate(across(c(nonrankbased,rankbased_asymptotic, rankbased_level2bs, independent, bonferroni), round, 3)) 
```


```{r nonrank-cov-plot, fig.cap = "Simulation Result for Coverage of Unordered Parameters"}
forplot <- prepare_coverage_data_plot(eq_res, bl_res, unordered = TRUE)
create_plot_for_coverage(forplot, unordered=TRUE)
```

The same coverage values are observed for different spreads of the true parameter vector $\boldsymbol{\theta}$. This results from assuming the same known $\Sigma$ across cases. In Equation (\ref{eq:prb}), it follows that the distribution of $t$ only depends on $\Sigma$ and $K$. This is more intuitive in the bootstrap world as demonstrated in Algorithm \ref{alg:nonrank_ci}. In step 2, we generate $\hat {\boldsymbol \theta}^*_b \sim N_K (\hat{\boldsymbol \theta}, \Sigma)$ and compute $\underset{k}{\max} \left| \frac{\hat{\theta}_{bk}^* - \hat{\theta}_k}{\sigma_k} \right|$ where $\hat{\boldsymbol \theta}_{b}^* - \hat{\boldsymbol \theta} \sim N_K(0, \Sigma)$. From Equation (\ref{eq:sigma_matrix}), this also implies that the correlation matrix $\mathbf{R}$ influences the coverage. 

Results for $T_1$ and $T_2$ tightness measures for $\mathbf{R}_{\text{eq}}$, shown in rows 1 and 2 of Figure \ref{fig:nonrank-plot}, indicate that Algorithm \ref{alg:nonrank_ci} yields narrower intervals than both the independent and Bonferroni approaches. The improvement is negligible at low $\rho$ and becomes more pronounced as $\rho$ increases; in each facet of Figure \ref{fig:nonrank-plot}, this is captured by the bend as each line connecting the points goes from `r IND$SHORTNAME`, `r BONF$SHORTNAME`, to `r NONRANK$SHORTNAME`. The angle of the bend in each facet also shows that the improvement in `r T1$MATHNAME` and `r T2$MATHNAME` is larger with lower variance in the estimates. Moreover, while intervals become wider with larger $K$, as shown by the groupwise movement of the points from the left to the right facet for each row of Figure \ref{fig:nonrank-plot}, this effect is dampened by the variance of the estimates. That is, the general increase in `r T1$MATHNAME` and `r T2$MATHNAME` as $K$ increases is larger for estimates that vary less. This is demonstrated by the corresponding jumps of each group of same-size points across facets for every row. When $\hat{\theta}$ values are more dispersed, the intervals are narrower; however, as they vary less or become closer to each other, ranks tend to interchange more, resulting in wider ranges. This aligns with the intuition that intervals are most precise when the estimates being ranked have greater separation. The same observations can be made for `r T3$MATHNAME` noting that higher values are more desirable. Altogether, these trends show that the proposed approach is most advantageous in the presence of moderate to high correlation, especially when ranking a larger number of estimates with close values.

The last three rows of Figure \ref{fig:nonrank-plot} show the results for a block diagonal correlation structure. Similar to the coverage results, the overall benefit of using the `r NONRANK$SHORTNAME` is reduced compared to when an equicorrelated structure is enforced. In each facet, this is illustrated through the muted bend of the line connecting the points corresponding to `r BONF$SHORTNAME` and the `r NONRANK$SHORTNAME`. Otherwise, the patterns observed for the equicorrelated structure remain consistent.

```{r nonrank-plot,fig.pos = "!htbp", fig.cap = "Simulation Result for Tightness Measure of Unordered Parameters", fig.height=8.75}
create_plot_for_t(prepare_t_facet_plot_data(
    eq_data = eq_res,
    bl_data = bl_res,
    unordered = TRUE), unordered = TRUE)
```

The coverage values corresponding to Figure \ref{fig:nonrank-cov-plot} and the values for $T_1$, $T_2$ and $T_3$ in Figure \ref{fig:nonrank-plot} are provided in Tables \ref{tab:nonrank-eq-cov} and \ref{tab:nonrank-eq-t1}–\ref{tab:nonrank-eq-t3}, respectively, in the Appendix.

## Joint confidence region for the ordered parameters {#sec:ordered-results}


Figures \ref{fig:rank-cov-plot} and \ref{fig:rank-plot} are similar to plots introduced in the previous section but show joint confidence regions for the ordered parameters namely, `r ASYMP$SHORTNAME` and `r BOOT$SHORTNAME`. With confidence regions for ranks, we are not able to map the intervals to the estimates.

The first column of Figure \ref{fig:rank-cov-plot} illustrates how coverage for `r ASYMP$SHORTNAME` deviates from the nominal level. The deviation is almost always negative, indicating that `r ASYMP$SHORTNAME` is mostly anti-conservative. Undercoverage is largest when the estimates being ranked are widely spread, but the deviation is somewhat smaller for large K (e.g., K=50), though it rarely reaches nominal coverage. For a block diagonal correlation structure (rows 2, 4, 6 of column 1), this slight reduction in deviation for K=50 can also be seen for low and moderate estimate variances. Otherwise, results do not vary systematically across correlation structures. Some cases with intermediate K (e.g., K=20 in row 4) show smaller deviation from nominal for B2, UL3, and UH3 compared to U2, illustrating that coverage can vary non-uniformly across different ranks and correlation settings.

The second column of Figure \ref{fig:rank-cov-plot} presents coverage for `r BOOT$SHORTNAME`. It produces values that do not deviate systematically from 0.95 but relatively closer when compared to `r ASYMP$SHORTNAME`. Except from the similar conservative joint confidence regions for $K=50$ across different levels of variances in the estimates for the block diagonal correlation structure, no other patterns are observed.

With the two proposed approaches, it is clear that `r BOOT$SHORTNAME` is superior to `r ASYMP$SHORTNAME` in terms of coverage. The former yields coverage closer to nominal irrespective of how correlated the estimates are.

```{r rank-cov-plot, fig.cap = "Simulation Result for Coverage of Ordered Parameters", fig.height = 7}
forplot <- prepare_coverage_data_plot(eq_res, bl_res, unordered = FALSE)
create_plot_for_coverage(forplot, unordered=FALSE)
```

Figure \ref{fig:rank-plot} shows the resulting tightness measures for the joint confidence regions of ordered parameters. Its first three rows are for `r ASYMP$SHORTNAME` while the last three rows are for `r BOOT$SHORTNAME`.

Regions become wider with larger $K$ as shown by the upward, groupwise movement of points from left to right in the first, second, fourth, and fifth rows of Figure \ref{fig:rank-plot}. For each facet, the widest regions correspond to estimates with low variance. 

```{r rank-plot, fig.cap = "Simulation Result for Tightness Measure of Ordered Parameters", fig.height=8.75}
create_plot_for_t(prepare_t_facet_plot_data(
    eq_data = eq_res,
    bl_data = bl_res,
    unordered = FALSE), unordered = FALSE)
```

Across different levels of $\rho$ in the equicorrelated structure, the difference in tightness measures become more pronounced with larger $K$ and lower variance. These differences are less noticeable for the block correlation structure where correlation is generally weaker. 

These findings are all consistent with the outcomes for the unordered parameters.

Despite its low coverage, `r ASYMP$SHORTNAME` still produces regions that are wider than those of `r BOOT$SHORTNAME`. This can be observed by comparing the range of y-axis values in the first and third rows for $T_1$ and also the second and fourth rows for $T_2$. Also, for equicorrelated structures, `r ASYMP$SHORTNAME` always logs wider regions for higher $\rho$.

The Appendix provides the coverage values for Figure \ref{fig:rank-cov-plot} (Table \ref{tab:rank-eq-cov}) and the values of $T_1$, $T_2$, and $T_3$ in Figure \ref{fig:rank-plot} (Tables \ref{tab:rank-eq-t1}–\ref{tab:rank-eq-t3}).



