We demonstrate the application of our proposed approaches to actual data using estimates from the Pulso ng Bayan Pre-electoral Survey (May 6–9, 2025). We also incorporate mean travel time to work, following a use case previously analyzed by Klein. In this research, we do not estimate correlation but instead assume potential sources and values. This aims to show that using an additional source of information can improve joint confidence regions by reducing overall uncertainty.

## Pulse Asia Results

For the Pulse Asia results, correlations are assumed to be driven by political slates and alliances formed for the elections. To show how overall uncertainty can be reduced when accounting for these correlations, we assume a block diagonal correlation structure and let $\rho$ vary from 0 to 0.9. This means that candidates within the same block move together, as their support levels are influenced by shared political slates and alliances. For the standard error, we use $\widehat {se} = \sqrt{\frac{\hat{p}_k(1-\hat{p}_k)}{n}}$ where $\hat{p}_k$ is the proportion of voters favoring candidate $k$ and $n=1,200$ is the sample size used by Pulse Asia for their survey. These are all that we need to construct the joint confidence region.

The analysis considers several key blocks: Alyansa, representing candidates campaigned for by the incumbent president, and DuterTen, composed of the vice-president and former president’s allies. Imee Marcos and Camille Villar are placed in a separate block, as both are endorsed by these rival factions. 

The Makabayan coalition is given its own category due to its large 11-candidate lineup, while the KiBam alliance highlights the partnership between Kiko Pangilinan and Bam Aquino. Other blocks include candidates focused on labor advocacies, independent popular senatoriables, and traditional politicians with experience in various executive departments. Finally, the remaining less prominent candidates are grouped into a single sectoral block.

Table \@ref(tab:pulse-table) shows that higher within-block correlation leads to better `r T1$MATHNAME`, `r T2$MATHNAME`, and `r T3$MATHNAME`. This means that, overall, the intervals in the joint confidence region are narrower, and therefore less uncertain. This is aligned to the results of the simulation as discussed in Section \ref{sec:unordered-results}.

```{r}
source("/home/realiseshewon/PDev/kde-ranking/R/CONSTANTS.R")
source("/home/realiseshewon/PDev/kde-ranking/R/generate_true_theta.R")
source("/home/realiseshewon/PDev/kde-ranking/R/simulate/compute_ci.R")
source("/home/realiseshewon/PDev/kde-ranking/R/simulate/compute_metrics.R")
source("/home/realiseshewon/PDev/kde-ranking/R/calculate_ci_application.R")
source("/home/realiseshewon/PDev/kde-ranking/R/preprocess_data.R")
source("/home/realiseshewon/PDev/kde-ranking/R/create_plot.R")
source("/home/realiseshewon/PDev/kde-ranking/R/create_table.R")
library(kableExtra)
library(tidyr)
library(dplyr)
```




```{r}
cand <- generate_true_theta_rd(persist_df = FALSE) %>% filter(`Voting For` >= 1)

cand$Makabayan <- ifelse(cand$Party == 'MKBYN', 1, 0)

# corr_matrix <-  block_corr(block_sizes=c(2, 12, 10, 2, 11, 2, 3, 3, 19), rho_within=c(rep(0.9,2), rep(0.9, 7)), rho_between=0.0)
corr_matrix <-  block_corr(block_sizes=c(2, 12, 10, 2, 11, 2, 3, 3, 6), rho_within=c(rep(0.9,2), rep(0.9, 7)), rho_between=0.0)
#generate_corr_mat(0.9, "pulse")



# dataset_all <- cand %>%
#   mutate(Voting_for_dec = `Voting For`/100) %>%
#   #filter(Voting_for_dec >= 0.01) %>%
#   mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
#   select(-Voting_for_dec) %>% 
#   arrange(desc(`Voting For`)) %>%  
#   arrange(desc(DuterTen), desc(Alyansa),desc(KiBam), desc(Makabayan))  %>%
#   rename(`Rank UB_pulse` = `Rank UB`, `Rank LB_pulse` = `Rank LB`)

dataset_all <- cand %>%
  # arrange(Party) %>%
  mutate(
    ind_name_recall = ifelse(Candidate %in% c(
      'Tulfo.B, Ben Bitag',
      'Revillame, Willie Wil'), 1, 0),
    ind_name_trad = ifelse(Candidate %in% c(
      'Bosita, Colonel',
      'Mendoza, Heidi',
      'Gonzales, Norberto'), 1, 0),
    labor = ifelse(Candidate %in% c(
      'Matula, Atty. Sonny',
      'Espiritu, Luke',
      'De Guzman, Ka Leody'
    ),1,0),
    sectoral = ifelse(Candidate %in% c(
      "D'Angelo, David", "Cabonegro, Roy", "Amad, Wilson", "Marquez, Norman", "Martinez, Eric",          
      "De Alban, Atty. Angelo", "Ballon, Roberto",  "Gamboa, Mark Louie", "Sahidulla, Nur-Ana", "Montemayor, Joey",
      "Valbuena, Mar Manibela", "Olivar, Jose Jessie", "Verceles, Leandro", "Jose, Relly Jr.", "Arellano, Ernesto",  
      "Escobal, Arnel", "Tapado, Michael BongBong", "Capuyan, Allen", "Mustapha, Subair"
    ),1, 0),
    )%>% 
  mutate(summed = DuterTen + Alyansa + KiBam + Makabayan + ind_name_recall + ind_name_trad + labor + sectoral) %>%
  mutate(Voting_for_dec = `Voting For`/100) %>%
  #filter(Voting_for_dec >= 0.01) %>%
  mutate(se = sqrt((Voting_for_dec*(1-Voting_for_dec))/1200) ) %>%
  select(-Voting_for_dec) %>% 
  arrange(desc(`Voting For`)) %>%  
  arrange(desc(DuterTen), desc(Alyansa),desc(KiBam), desc(Makabayan), desc(ind_name_recall), desc(ind_name_trad), desc(labor), desc(sectoral))  %>%
  rename(`Rank UB_pulse` = `Rank UB`, `Rank LB_pulse` = `Rank LB`)
```



```{r}

  


# ci_results <- get_ci_for_app_data(
#     theta_hat = (dataset_all$`Voting For`)/100,
#     true_sds = dataset_all$se,
#     K = dim(dataset_all)[1],
#     alpha = 0.05,
#     B <- 500,
#     corr_matrix=corr_matrix 
#     )
```



```{r pulse-table}
# all_ci <- lapply(seq(0,0.9,0.1), function(r){
#   
#   corr_matrix <- generate_corr_mat(r, "pulse")
#   
#   ci_results <- get_ci_for_app_data(
#     theta_hat = (dataset_all$`Voting For`)/100,
#     true_sds = dataset_all$se,
#     K = dim(dataset_all)[1],
#     alpha = 0.05,
#     B <- 500,
#     corr_matrix=corr_matrix 
#     )
#   
#   out <- get_tmeasures_for_app_data(ci_results)
#   out$r <- r
#   
#   return(out %>% select(r, Measure, Independent, Bonferroni, Nonrank, Asymptotic, Level2bs))
#   })
# 
# allcases <- do.call(rbind, all_ci)

# to_table <- allcases %>% 
#   pivot_longer(cols = c(Independent, Bonferroni, Nonrank), 
#                           names_to = "Approach", 
#                           values_to = "Value") %>% 
#   distinct() %>%
#   pivot_wider(names_from = 'Measure',values_from = "Value") %>% 
#   filter(!((Approach == 'Bonferroni' | Approach == 'Independent') & r != 0 )) %>% 
#   mutate(Approach = tolower(Approach)) %>%
#   mutate(Approach = ifelse(Approach == 'nonrank', 'nonrankbased', Approach)) %>%
#   mutate(across(c(T1, T2, T3), round, 3)) #%>%#%>% 
#   #distinct(Approach, T1, T2, T3, .keep_all = TRUE)
# 
# create_basic_results_table(to_table, "Joint Confidence Region Tightness Measures")
```





```{r}
# my_list <- list(t_values = allcases, all_ci = ci_results)
# saveRDS(my_list, file = "filtered-to-one-pulse-CI.rds")
pulse_ci <- readRDS("filtered-to-one-pulse-CI.rds")
```

```{r}
# all_ci <- lapply(seq(0,0.9,0.1), function(r){
#   
#   corr_matrix <- generate_corr_mat(r, "pulse")
#   
#   ci_results <- get_ci_for_app_data(
#     theta_hat = (dataset_all$`Voting For`)/100,
#     true_sds = dataset_all$se,
#     K = dim(dataset_all)[1],
#     alpha = 0.05,
#     B <- 500,
#     corr_matrix=corr_matrix 
#     )
#   
#   out <- get_tmeasures_for_app_data(ci_results)
#   out$r <- r
#   
#   return(out %>% select(r, Measure, Independent, Bonferroni, Nonrank))
#   })
# 
# allcases <- do.call(rbind, all_ci)
# 
# to_table <- allcases %>% 
#   pivot_longer(cols = c(Independent, Bonferroni, Nonrank), 
#                           names_to = "Approach", 
#                           values_to = "Value") %>% 
#   distinct() %>%
#   pivot_wider(names_from = 'Measure',values_from = "Value") %>% 
#   filter(!((Approach == 'Bonferroni' | Approach == 'Independent') & r != 0 )) %>% 
#   mutate(Approach = tolower(Approach)) %>%
#   mutate(Approach = ifelse(Approach == 'nonrank', 'nonrankbased', Approach)) %>%
#   mutate(across(c(T1, T2, T3), round, 3)) #%>%#%>% 
#   #distinct(Approach, T1, T2, T3, .keep_all = TRUE)
# 
# create_basic_results_table(to_table, "Joint Confidence Region Tightness Measures")
```




```{r}
p <- function(v) {
  Reduce(f=paste, x = v)
}
```


```{r}
prepared_data <-  prepare_plotting_data_for_pulse(pulse_ci$all_ci,dataset_all) %>%
  mutate(Approach = ifelse(Approach == 'nonrank', 'nonrankbased', Approach)) %>%
  separate(
    col = Candidate,           
    into = c("Candidate", "FirstName"),
    sep = ",",    
    extra = "merge"
  ) %>% filter(Approach != "bonferroni")# %>% filter(Approach != "pulse")


diffs <- prepared_data %>% 
  group_by(Approach, highlight1, Candidate,) %>% 
  count() %>% 
  filter(Approach != 'pulse')%>%
  pivot_wider(names_from = Approach, values_from = n) %>% 
  mutate(diff = independent - nonrankbased) %>% arrange(desc(diff)) %>%
  pivot_longer(cols = c(independent, nonrankbased), names_to='Approach') %>%
  mutate(diff = ifelse(Approach=="nonrankbased", diff, 0))
```

```{r}
# DAT <- dataset_all %>% separate(Candidate, into = c("Candidate", "f"), sep = ", ")
# diffs %>% filter(Approach == 'nonrankbased') %>% left_join(DAT[,c("Candidate", "se", "Voting For")]) %>% select(-value) %>% arrange(highlight1, se) %>%View()
```


```{r pulse-asia-fig,fig.cap = "Tightness Measures for Pulse Asia Results Across $\\rho$", fig.height = 3.5}
create_plot_for_t_app_plot(pulse_ci$t_values)
```


To show how the improvement gets reflected into the joint confidence region, we assume a high correlation ($\rho = 0.9$) within each previously enumerated block and visually compare the joint confidence regions. Note that lower rank corresponds to highly preferred candidates. The first facet of Figure \@ref(fig:pulse-result) illustrates the `r IND$SHORTNAME` joint confidence region while the second one shows the improved `r NONRANK$SHORTNAME` joint confidence region. The green-shaded shapes are the intervals that got lesser occupied positions after accounting for the correlation. The darker the shade is, the higher the reduction in length. There is no distinguishable pattern as to which among each block members get an improved interval length, but the highest improvement is seen to occur in the middle part of the ranked estimates. `r BONF$SHORTNAME` is not included as it is hugely similar to `r IND$SHORTNAME`.


```{r pulse-result,fig.cap = "95% Joint Confidence Region for Senatoriable Preferences", fig.height = 7}
prepared_data <-  prepare_plotting_data_for_pulse(pulse_ci$all_ci,dataset_all) %>%
  mutate(Approach = ifelse(Approach == 'nonrank', 'nonrankbased', Approach)) %>%
  separate(
    col = Candidate,           
    into = c("Candidate", "FirstName"),
    sep = ",",    
    extra = "merge"
  ) %>% filter(Approach != "bonferroni")# %>% filter(Approach != "pulse")

prepared_data1 <- prepared_data %>% left_join(diffs[,c("Approach", "Candidate", 'diff')], by = c("Approach", "Candidate"))

create_plot_for_app_data(prepared_data1, Candidate, k, reverse=TRUE,
                         # title ='95% Joint Confidence Region for Candidates with at least 1% Votes', 
                        shape_map = c("DuterTen" = 0, "Alyansa" = 1, "KiBam" = 2, "Makabayan" = 3,
                                      "DuterTen-Alyansa" = 8, "Traditional" = 5, "Media" = 6, 'Labor' = 10, 'Sectoral' = 4))
```


## 2011 Mean Travel Time to Work in the US

We employ a similar assumption of a block diagonal correlation structure induced by population density levels across states. As @klein observed in their analysis of this data, states with higher population densities tend to report longer travel times to work. Five blocks are used, wherein the first has population density from 0 to 20 people per square mile, the second has 20 to 50, the third has 50 to 100, the fourth has 100 to 200, and the fifth has more than 200. We construct the joint confidence region when $\rho$ is varied from $0.0$ up to $0.9$. For simplicity, we assume the same $\rho$ across all blocks. 

```{r}
dataset_all <- readRDS("/home/realiseshewon/PDev/kde-ranking/data/mean_travel_time_ranking_2011.rds")
```


```{r}
dataset_all <- readRDS("/home/realiseshewon/PDev/kde-ranking/data/mean_travel_time_ranking_2011.rds")

dataset_all$region <- c("South", "West", "West", "South", "West", "West", "Northeast", "South", "South", "South", "South", "West", "West", "Midwest", "Midwest", "Midwest", "Midwest", "South", "South", "Northeast", "South", "Northeast", "Midwest", "Midwest", "South", "Midwest", "West", "Midwest", "West", "Northeast", "Northeast", "West", "Northeast", "South", "Midwest", "Midwest", "South", "West", "Northeast", "Northeast", "South", "Midwest", "South", "South", "West", "Northeast", "South", "West", "South", "Midwest", "West")


dataset_all$density <- c(94.4, 1.2, 56.3,
                      56.0, 239.1, 48.5,
                      738.1, 460.8, 9856.5,
                      350.6,168.4,211.8,
                      19.0,	231.1,181.0,
                      54.5,34.9,109.9,
                      104.9,43.1,594.8,
                      839.4,174.8,66.6,
                      63.2,87.1, 6.8,
                      23.8, 24.6, 147.0,
                      1195.5,17.0, 411.2,
                      196.1, 9.7, 282.3,
                      54.7, 39.9, 283.9,
                      1018.1,153.9,10.7,
                      153.9,96.3,	33.6,
                      67.9, 202.6, 101.2,
                      77.1, 105.0, 5.8)


dataset_all <- dataset_all %>% mutate(
  density_group = ifelse(density > 0 & density <= 20, 1,
                         ifelse(density > 20 & density <= 50, 2,
                                ifelse(density > 50 & density <= 100, 3,
                                       ifelse(density > 100 & density <= 200, 4, 5))))
) %>% arrange(desc(theta_k)) %>% 
  arrange(desc(region))
  #arrange(desc(density_group))
```



```{r}
# all_ci <- lapply(seq(0,0.9,0.1), function(r){
# 
#   corr_matrix <- generate_corr_mat(r, "traveltime")
# 
#   ci_results <- get_ci_for_app_data(
#     theta_hat = dataset_all$theta_k,
#     true_sds = dataset_all$S,
#     K = dim(dataset_all)[1],
#     alpha = 0.05,
#     B <- 500,
#     corr_matrix=corr_matrix
#     )
# 
#   out <- get_tmeasures_for_app_data(ci_results)
#   out$r <- r
# 
#   return(out %>% select(r, Measure, Independent, Bonferroni, Nonrank, Asymptotic, Level2bs))
#   })

# allcases <- do.call(rbind, all_ci)
```

```{r}
allcases <- readRDS("all-travel-time-CI.rds")
```




```{r}
to_table <- allcases$t_values %>%
  pivot_longer(cols = c(Independent, Bonferroni, Nonrank),
                          names_to = "Approach",
                          values_to = "Value") %>%
  distinct() %>%
  pivot_wider(names_from = 'Measure',values_from = "Value") %>%
  filter(!((Approach == 'Bonferroni' | Approach == 'Independent') & r != 0 )) %>%
  mutate(Approach = tolower(Approach)) %>%
  mutate(Approach = ifelse(Approach == 'nonrank', 'nonrankbased', Approach)) %>%
  mutate(across(c(T1, T2, T3), round, 3)) %>%
  select(-c(Asymptotic, Level2bs))
```


```{r}
coeffcons <- 0.9
# corr_matrix <-generate_corr_mat(coeffcons, "traveltime")
# 
# ci_results <- get_ci_for_app_data(
#   theta_hat = dataset_all$theta_k,
#   true_sds = dataset_all$S,
#   K = dim(dataset_all)[1],
#   alpha = 0.05,
#   B <- 500,
#   corr_matrix=corr_matrix
#   )
# 
# my_list <- list(t_values = allcases, all_ci = ci_results)
# saveRDS(my_list, file = "my_objects.rds")
```


```{r}
# my_list <- list(t_values = allcases, all_ci = ci_results)
# saveRDS(my_list, file = "all-travel-time-CI.rds")
```





```{r}
prepared_data <- prepare_plotting_data_for_traveltime(allcases$all_ci,
                                                      dataset_all, unordered = TRUE) %>%
  mutate(Approach = ifelse(Approach == 'nonrank', 'nonrankbased', Approach))


diffs <- prepared_data %>% 
  group_by(Approach, highlight1, iso,) %>% 
  count() %>% 
  filter(Approach != 'pulse')%>%
  pivot_wider(names_from = Approach, values_from = n) %>% 
  mutate(diff = independent - nonrankbased) %>%
  arrange(desc(diff)) %>%
  #pivot_longer(cols = c(asymptotic, level2bs), names_to='Approach') %>%
  pivot_longer(cols = c(bonferroni, nonrankbased), names_to='Approach') %>%
  mutate(diff = ifelse(Approach=="nonrankbased", diff, 0))

```


```{r}
t1_after <- to_table[[which(to_table$r == coeffcons & to_table$T1 & to_table$Approach == NONRANK$RAWCHAR), "T1"]]
t1_before <- to_table[[which(to_table$r == 0.0 & to_table$T1 & to_table$Approach == BONF$RAWCHAR), "T1"]]
t2_after <- to_table[[which(to_table$r == coeffcons & to_table$T2 & to_table$Approach == NONRANK$RAWCHAR), "T2"]]
t2_before <- to_table[[which(to_table$r == 0.0 & to_table$T2 & to_table$Approach == BONF$RAWCHAR), "T2"]]
t3_after <- to_table[[which(to_table$r == coeffcons & to_table$T3 & to_table$Approach == NONRANK$RAWCHAR), "T3"]]
t3_before <- to_table[[which(to_table$r == 0.0 & to_table$T3 & to_table$Approach == BONF$RAWCHAR), "T3"]]
t2_improvement <- round(((t2_before-t2_after)/t2_before)*100, 2)
t1_improvement <- round(((t1_before-t1_after)/t1_before)*100, 2)
t3_improvement <- round(((t3_after-t3_before)/t3_before)*100, 2)
```

Figure \@ref(fig:travel-time-fig) shows how `r T1$MATHNAME`, `r T2$MATHNAME`, and `r T3$MATHNAME` for `r NONRANK$SHORTNAME` start continuously improving from $\rho = 0.4$ up to $0.9$, when compared to those of `r BONF$SHORTNAME` and `r IND$SHORTNAME`. This is consistent to the simulation findings in Section \ref{sec:ordered-results}. We see that the largest improvement is attained with higher $\rho$. In the presence of $\rho = `r coeffcons`$, `r T1$MATHNAME` reduces by `r t1_improvement`% to `r t1_after` when using `r NONRANK$SHORTNAME` from `r t1_before` when using `r BONF$SHORTNAME` to construct the joint confidence region. `r T2$MATHNAME` also improves by `r t2_improvement`% from `r t2_before` to `r t2_after` while  `r T3$MATHNAME` by `r t3_improvement`% from `r t3_before` to `r t3_after`. The actual values are provided in Table \@ref(tab:travel-time-tab-nonrank) in the Appendix.

```{r travel-time-fig,fig.cap = "Tightness Measures for Mean Travel Time to Work Across $\\rho$", fig.height = 3.5}
create_plot_for_t_app_plot(allcases$t_values)
```

Figure \@ref(fig:travel-time-fig-nonrank) illustrates how `r T1$MATHNAME`, `r T2$MATHNAME`, and `r T3$MATHNAME` affect the resulting joint confidence region for `r BONF$SHORTNAME` and `r NONRANK$SHORTNAME` when $\rho = `r coeffcons`$. Only joint confidence regions for `r BONF$SHORTNAME` and `r NONRANK$SHORTNAME` are shown since the `r IND$SHORTNAME` result is similar to that of `r BONF$SHORTNAME`. Lower rank corresponds to states with lower mean travel time. It can be observed that those with no decrease in occupied rank positions originally occupy fewer rank positions (two to seven) than those whose occupied positions (five to 20) decrease by 2 to 3.

```{r}
# dataset_all %>% left_join(prepared_data1 %>% filter(Approach == 'nonrankbased') %>% select(iso, diff)  %>% distinct(),
#                         by = 'iso') %>%
# mutate(range_l = bonf_rank_upper - bonf_rank_lower + 1) %>%
# arrange(desc(diff)) %>% group_by(density_group) %>% mutate(meansd = median(S)) %>% arrange(density_group) %>% pull(theta_k) %>%sd
```



```{r travel-time-fig-nonrank, fig.cap = "95% Joint Confidence Region for 2011 Mean Travel Time To Work in the US", fig.height = 7}
prepared_data1 <- prepared_data %>% left_join(diffs[,c("Approach", "iso", 'diff')], by = c("Approach", "iso"))
create_plot_for_app_data(prepared_data1 %>%
                           filter(Approach != 'independent'), iso, theta_k, reverse=FALSE,xlab = "State",
                         # title = "95% Joint Confidence Region for 2011 Mean Travel Times in the US",
                         shape_legend_title ="Region",
                         # shape_labels = c("Midwest", "Northeast", "South", "West"),
                         # shape_map = c("Midwest" = 0, "Northeast" = 1, "South" = 2, "West" = 6)
                         shape_labels = c("0-20", "20-50", "50-100", "100-200","200+"),
                         shape_map = c("1" = 0, "2" = 1, "3" = 2, "4" = 6,"5" = 3)
                         )
```






https://www.energy.gov/cmei/vehicles/fact-661-february-7-2011-population-density