```{r}
source("/home/realiseshewon/PDev/kde-ranking/R/create_plot.R")
dataset<-readRDS("/home/realiseshewon/PDev/kde-ranking/data/true_theta.rds")
```

## Simulation True $\boldsymbol \theta$s

```{r tab.cap="True $\\theta$ values used in the simulation have different levels of variability.", include = FALSE}

source("/home/realiseshewon/PDev/kde-ranking/R/create_table.R")
create_table_for_true_theta(
dataset %>% 
  select(K, data_spread, true_theta) %>%
  group_by(K, data_spread) %>%
  summarise(true_theta = paste(round(true_theta, 1), collapse = ", "), .groups = "drop") %>%
  mutate(R = "$\\mathbf{R}_{eq, \\rho} = 0.1, 0.5, 0.9$ $\\mathbf{R}_{block} - 2, 3$ blocks")
)
```


```{r true-theta-boxplot, fig.cap="True $\\theta$ values used in the simulation have different levels of variability.", message = FALSE, warning=FALSE, fig.pos='H'}
source("/home/realiseshewon/PDev/kde-ranking/R/create_plot.R")

dataset<-readRDS("/home/realiseshewon/PDev/kde-ranking/data/true_theta.rds")
create_boxplot_for_true_theta(dataset)
```




```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
source("/home/realiseshewon/PDev/kde-ranking/R/preprocess_data.R")
source("/home/realiseshewon/PDev/kde-ranking/R/preprocess_data.R")
source("/home/realiseshewon/PDev/kde-ranking/R/create_table.R")
source("/home/realiseshewon/PDev/kde-ranking/R/create_plot.R")
source("/home/realiseshewon/PDev/kde-ranking/R/CONSTANTS.R")

# equicorr <- TRUE
# eq_res <- combine_summaries(
#   "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_k",
#   TRUE
# ) %>%  mutate(across(5:9, round, 3))
# 
# 
# bl_res <- combine_summaries(
#   "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_block",
#   FALSE
# ) %>%  mutate(across(5:9, round, 3))


eq_res <- combine_summaries(
  "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_k",
  TRUE
) %>% mutate(Variance = factor(ifelse(sd == 2, 'Low', 
                                      ifelse(sd == 3.6, "Moderate", "High")),
                               levels = c("Low", "Moderate", "High"), 
                               ordered = TRUE)) %>% 
  mutate(`Correlation structure` = "Equicorrelated")  %>%
  mutate(across(c(nonrankbased,rankbased_asymptotic, rankbased_level2bs, 
                  independent, bonferroni), round, 3)) 
  #mutate(across(5:8, round, 3))


bl_res <- combine_summaries(
  "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_block",
  FALSE
) %>% 
mutate(
  Variance = factor(ifelse(sd == 2, 'Low', 
                    ifelse(sd == 3.6, "Moderate", "High")),
                    levels = c("Low", "Moderate", "High"), 
                    ordered = TRUE),
  
  r = factor(
    case_when(
      r == "balanced-block" & blocks == 2 ~ "B2",
      r == "unbalanced-block" & blocks == 2 ~ "U2",
      r == "unbalanced-block" & blocks == 3 ~ "UL3",
      r == "unbalanced-block-high" & blocks == 3 ~ "UH3",
      TRUE ~ r
    ),
    levels = c("B2", "U2", "UL3", "UH3"),
    ordered = TRUE
  )
) %>% 
    mutate(`Correlation structure` = "Block Diagonal") %>%
  mutate(across(c(nonrankbased,rankbased_asymptotic, rankbased_level2bs, 
                  independent, bonferroni), round, 3)) 
```

\newpage

\vspace*{1cm}

## Tables: Joint Confidence Region for the Unordered Parameters

```{r nonrank-eq-cov}
options(knitr.kable.NA = '')
eq_coverage_unordered <- preprocess_coverage(eq_res, sd_value = 2, 
                                             equicorrelation = TRUE,
                                             unordered = TRUE)
bl_coverage_unordered <- preprocess_coverage(bl_res, sd_value = 2, 
                                             equicorrelation = FALSE, 
                                             unordered = TRUE)
create_side_by_side_table_within_main(eq_data = eq_coverage_unordered,
                           bl_data = bl_coverage_unordered, 
                          num_variance=1,
                          unordered = TRUE
                                      )
```


\blandscape

\newpage
\vspace*{1cm}


```{r nonrank-eq-t1}
options(knitr.kable.NA = "")

create_table_for_tightness_measure(prepare_appendix_t_measure_table(
  eq_res, bl_res, unordered=TRUE, tmeasure = "t1"),
  "t1", unordered = TRUE)

```

\newpage
\vspace*{1cm}

```{r nonrank-eq-t2}
options(knitr.kable.NA = "")

create_table_for_tightness_measure(prepare_appendix_t_measure_table(
  eq_res, bl_res, unordered=TRUE, tmeasure = "t2"),
  "t2", unordered = TRUE)

```

\newpage
\vspace*{1cm}

```{r nonrank-eq-t3}
options(knitr.kable.NA = "")
create_table_for_tightness_measure(prepare_appendix_t_measure_table(
  eq_res, bl_res, unordered=TRUE, tmeasure = "t3"),
  "t3", unordered = TRUE)
```

\newpage

\vspace*{1cm}

## Tables: Joint Confidence Region for the Ordered Parameters

```{r rank-eq-cov}
options(knitr.kable.NA = "")

eq_coverage_ordered1 <- preprocess_coverage(eq_res, sd_value = 2, 
                                            equicorrelation = TRUE, 
                                            unordered = FALSE)
bl_coverage_ordered1 <- preprocess_coverage(bl_res, sd_value = 2,
                                            equicorrelation = FALSE, 
                                            unordered = FALSE)
eq_coverage_ordered2 <- preprocess_coverage(eq_res, sd_value = 3.6, 
                                            equicorrelation = TRUE, 
                                            unordered = FALSE)
bl_coverage_ordered2 <- preprocess_coverage(bl_res, sd_value = 3.6, 
                                            equicorrelation = FALSE, 
                                            unordered = FALSE)
eq_coverage_ordered3 <- preprocess_coverage(eq_res, sd_value = 6, 
                                            equicorrelation = TRUE, 
                                            unordered = FALSE)
bl_coverage_ordered3 <- preprocess_coverage(bl_res, sd_value = 6, 
                                            equicorrelation = FALSE, 
                                            unordered = FALSE)
main <- rbind(
  rbind(eq_coverage_ordered1, bl_coverage_ordered1) %>% 
    mutate(sd = "Low"),
  rbind(eq_coverage_ordered2, bl_coverage_ordered2) %>% 
    mutate(sd = "Moderate"),
  rbind(eq_coverage_ordered3, bl_coverage_ordered3) %>%
    mutate(sd = "High")
)  %>% 
  pivot_longer(cols = c(rankbased_asymptotic, rankbased_level2bs),
               names_to = "app") %>%
  unite("app", app, sd, sep = "-", remove =TRUE) %>%
  pivot_wider(names_from = app,
              values_from = value)

create_table_for_tightness_measure(prepare_appendix_cov_measure_table(main), 
                                   "coverage", unordered = FALSE)
```


\newpage
\vspace*{1cm}


```{r rank-eq-t1}
options(knitr.kable.NA = "")
create_table_for_tightness_measure(prepare_appendix_t_measure_table(
  eq_res, bl_res, unordered=FALSE, tmeasure = "t1"), 
  "t1", unordered = FALSE)
```

\newpage
\vspace*{1cm}

```{r rank-eq-t2}
options(knitr.kable.NA = "")

create_table_for_tightness_measure(prepare_appendix_t_measure_table(
  eq_res, bl_res, unordered=FALSE, tmeasure = "t2"), 
  "t2", unordered = FALSE)
```


\newpage
\vspace*{1cm}

```{r rank-eq-t3}
options(knitr.kable.NA = "")
create_table_for_tightness_measure(prepare_appendix_t_measure_table(
  eq_res, bl_res, unordered=FALSE, tmeasure = "t3"),
  "t3", unordered = FALSE)
```

\elandscape
\newpage

\vspace*{1cm}

## Tables: Pulse Asia Tightness Measures

```{r travel-time-tab-nonrank}
allcases <- readRDS("filtered-to-one-pulse-CI.rds")
to_table <- prepare_data_for_application(allcases$t_values, unordered =TRUE)
create_basic_results_table(to_table, 
                           "Tightness Measures for Unordered Parameters")
```


```{r travel-time-tab-rank}
totab1 <- prepare_data_for_application(allcases$t_values, unordered =FALSE)
create_t_table_for_ordered_application(totab1)
```


\newpage

\vspace*{1cm}

## Tables: 2011 Mean Travel Time to Work in the US Tightness Measures

```{r travel-time-tab-nonrank2}
allcases <- readRDS("all-travel-time-CI.rds")
to_table <- prepare_data_for_application(allcases$t_values, unordered =TRUE)
create_basic_results_table(to_table, 
                           "Tightness Measures for Unordered Parameters")
```

```{r travel-time-tab-rank2}
allcases <- readRDS("all-travel-time-CI.rds")
totab1 <- prepare_data_for_application(allcases$t_values, unordered =FALSE)
create_t_table_for_ordered_application(totab1)
```
