---
number_sections: true
fig_caption: yes
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
indent: true
header-includes:
- \PassOptionsToPackage{colorlinks=true,linkcolor=blue,citecolor=black,urlcolor=black}{hyperref}
- \usepackage{amsmath}
- \numberwithin{equation}{section}
- \usepackage{setspace}\onehalfspacing
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{indentfirst}
- \usepackage{xparse}
- \usepackage{tcolorbox}
- \usepackage{algorithm}
- \usepackage{algpseudocode}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage{placeins}
- \renewcommand{\ttfamily}{\rmfamily}
- \usepackage{etoolbox}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{booktabs}
- \AtBeginEnvironment{algorithmic}{\setstretch{1.5}} 
- \renewcommand{\arraystretch}{0.75}
- \renewcommand{\multirowsetup}{\raggedright}
# --- Thesis font definition (change here once, affects everything) ---
- \usepackage{anyfontsize}
- \newcommand{\thesisfont}{\fontsize{20pt}{19pt}\selectfont}
- \thesisfont
- \usepackage{xcolor}
- \usepackage[colorlinks=true,linkcolor=blue,urlcolor=black,citecolor=black]{hyperref}
- \AtBeginDocument{\hypersetup{colorlinks=true,linkcolor=blue,citecolor=black,urlcolor=black}}
- \usepackage{titlesec}
- \titleformat{\section}{\fontsize{20pt}{22pt}\bfseries}{\thesection}{1em}{}
- \titleformat{\subsection}{\fontsize{18pt}{20pt}\bfseries}{\thesubsection}{1em}{}
- \titleformat{\subsubsection}{\fontsize{16pt}{19pt}\bfseries}{\thesubsubsection}{1em}{}
- \usepackage{caption}
- \captionsetup[figure]{font={large,bf}}
- \captionsetup[table]{font={large,bf}}
- \newcommand{\algfont}{\fontsize{15pt}{18pt}\selectfont} # slightly smaller than thesis font
- \DeclareCaptionFont{thesisalg}{\algfont\bfseries} # caption font
- \captionsetup[algorithm]{font=thesisalg}
- \AtBeginEnvironment{algorithm}{\algfont} # algorithm body
- \AtBeginEnvironment{algorithmic}{\algfont}   

papersize: a4
---

```{r echo = FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE
)
```


```{r}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```


```{r}
source("/home/realiseshewon/PDev/kde-ranking/R/create_plot.R")
dataset<-readRDS("/home/realiseshewon/PDev/kde-ranking/data/true_theta.rds")
```

## True $\theta$ Values Used in the Simulation

Figure \@ref(fig:true-theta-boxplot) shows how the spread of the $\theta$ varies in the cases considered in Table \@ref(tab:true-theta-table)

```{r tab.cap="True $\\theta$ values used in the simulation have different levels of variability.", include = FALSE}

source("/home/realiseshewon/PDev/kde-ranking/R/create_table.R")
create_table_for_true_theta(
dataset %>% 
  select(K, data_spread, true_theta) %>%
  group_by(K, data_spread) %>%
  summarise(true_theta = paste(round(true_theta, 1), collapse = ", "), .groups = "drop") %>%
  mutate(R = "$\\mathbf{R}_{eq, \\rho} = 0.1, 0.5, 0.9$ $\\mathbf{R}_{block} - 2, 3$ blocks")
)
```



```{r true-theta-boxplot, fig.cap="True $\\theta$ values used in the simulation have different levels of variability.", message = FALSE, warning=FALSE, fig.pos='H'}
source("/home/realiseshewon/PDev/kde-ranking/R/create_plot.R")

dataset<-readRDS("/home/realiseshewon/PDev/kde-ranking/data/true_theta.rds")
create_boxplot_for_true_theta(dataset)
```



```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
source("/home/realiseshewon/PDev/kde-ranking/R/preprocess_data.R")
source("/home/realiseshewon/PDev/kde-ranking/R/create_table.R")


equicorr <- TRUE
eq_res <- combine_summaries(
  "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_k",
  TRUE
) %>%  mutate(across(5:9, round, 3))


bl_res <- combine_summaries(
  "/home/realiseshewon/PDev/kde-ranking/simulation_results/summaries/summary_block",
  FALSE
) %>%  mutate(across(5:9, round, 3))
```


\blandscape



```{r}
# bl_res %>% filter(metric != "coverage") %>% #select(-c(rankbased_asymptotic,rankbased_level2bs)) %>%
#   mutate(r = paste(r, blocks, sep = '-')) %>%
#   mutate(r = case_when(
#     r == "balanced-block-2" ~ "B2",
#     r == "unbalanced-block-2" ~ "U2",
#     r == "unbalanced-block-3" ~ "UL3",
#     r == "unbalanced-block-high-3" ~ "UH3",
#     TRUE ~ r
#   ))%>% 
#   mutate(Variability =ifelse(sd==2.0, "low", ifelse(sd==3.6, "med", "high"))) %>% 
#   filter(metric == 't1') %>%
#   select(-c(sd, blocks, metric))%>%
#   pivot_wider(names_from = Variability,
#               values_from = c(independent,bonferroni,nonrankbased,rankbased_asymptotic,rankbased_level2bs),
#               names_sep = "-") %>% 
#   arrange(K, r)
```

```{r}
# bl_test<- bl_res %>% filter(metric != "coverage") %>% #select(-c(rankbased_asymptotic,rankbased_level2bs)) %>%
#   mutate(r = paste(r, blocks, sep = '-')) %>%
#   mutate(r = case_when(
#     r == "balanced-block-2" ~ "B2",
#     r == "unbalanced-block-2" ~ "U2",
#     r == "unbalanced-block-3" ~ "UL3",
#     r == "unbalanced-block-high-3" ~ "UH3",
#     TRUE ~ r
#   ))%>% 
#   mutate(Variability =ifelse(sd==2.0, "low", ifelse(sd==3.6, "med", "high"))) %>% 
#   filter(metric == 't1') %>%
#   select(-c(sd, blocks, metric))%>%
#   pivot_wider(names_from = Variability,
#               values_from = c(independent,bonferroni,nonrankbased,rankbased_asymptotic,rankbased_level2bs),
#               names_sep = "-") %>% 
#   arrange(K, r) %>%
#   select(r,
#     `independent-low`, `bonferroni-low`, `nonrankbased-low`,
#     `independent-med`, `bonferroni-med`, `nonrankbased-med`,
#     `independent-high`, `bonferroni-high`, `nonrankbased-high`)
# 
# tabb1 <- preprocess_tightness_measure(eq_res, "t1", equicorr)
# # 
# # if (!equicorr) {
# #   tabb1 <- tabb1 %>% select(-c(r, blocks))
# # }
# 
# tabb1 <- tabb1 %>% select(K, r,
#     independent_low, bonferroni_low, nonrankbased_low,
#     independent_med, bonferroni_med, nonrankbased_med,
#     independent_high, bonferroni_high, nonrankbased_high)
# 
# eq_padded_ordered <- tabb1 %>%
#   group_by(K) %>% # or whatever variable defines your 10, 20, 30 groups
#   group_modify(~ add_row(.x)) %>% 
#   ungroup()
# 
# cbind(eq_padded_ordered, bl_test)
```







```{r nonrank-eq-t1}
options(knitr.kable.NA = "")

create_table_for_tightness_measure(prepare_appendix_t_measure_table(eq_res, bl_res, unordered=TRUE, tmeasure = "t1"), 
                                   "t1", unordered = TRUE)

```
```{r nonrank-eq-t2}
options(knitr.kable.NA = "")

create_table_for_tightness_measure(prepare_appendix_t_measure_table(eq_res, bl_res, unordered=TRUE, tmeasure = "t2"), 
                                   "t2", unordered = TRUE)

```


```{r nonrank-eq-t3}
options(knitr.kable.NA = "")
create_table_for_tightness_measure(prepare_appendix_t_measure_table(eq_res, bl_res, unordered=TRUE, tmeasure = "t3"), 
                                   "t3", unordered = TRUE)

```





```{r rank-eq-t1}
options(knitr.kable.NA = "")

create_table_for_tightness_measure(prepare_appendix_t_measure_table(eq_res, bl_res, unordered=FALSE, tmeasure = "t1"), 
                                   "t1", unordered = FALSE)

```
```{r rank-eq-t2}
options(knitr.kable.NA = "")

create_table_for_tightness_measure(prepare_appendix_t_measure_table(eq_res, bl_res, unordered=FALSE, tmeasure = "t2"), 
                                   "t2", unordered = FALSE)

```


```{r rank-eq-t3}
options(knitr.kable.NA = "")
create_table_for_tightness_measure(prepare_appendix_t_measure_table(eq_res, bl_res, unordered=FALSE, tmeasure = "t3"), 
                                   "t3", unordered = FALSE)

```




```{r}
# tabb1 <- preprocess_tightness_measure(eq_res, "t2", equicorr, TRUE)
# 
# if (!equicorr) {
#   tabb1 <- tabb1 %>% select(-c(r, blocks))
# }
# 
# tabb1 <- tabb1 %>% select(K, r,
#     independent_low, bonferroni_low, nonrankbased_low,
#     independent_med, bonferroni_med, nonrankbased_med,
#     independent_high, bonferroni_high, nonrankbased_high,
#     rankbased_asymptotic_low, rankbased_level2bs_low,
#     rankbased_asymptotic_med, rankbased_level2bs_med,
#     rankbased_asymptotic_high, rankbased_level2bs_high)
# create_table_for_tightness_measure(
#   summary=tabb1,
#   metric_type="$T_2$",
#   equicorr)
```

```{r}
# tabb1 <- preprocess_tightness_measure(eq_res, "t2", equicorr, TRUE)
# 
# if (!equicorr) {
#   tabb1 <- tabb1 %>% select(-c(r, blocks))
# }
# 
# tabb1 <- tabb1 %>% select(K, r,
#     independent_low, bonferroni_low, nonrankbased_low,
#     independent_med, bonferroni_med, nonrankbased_med,
#     independent_high, bonferroni_high, nonrankbased_high,
#     rankbased_asymptotic_low, rankbased_level2bs_low,
#     rankbased_asymptotic_med, rankbased_level2bs_med,
#     rankbased_asymptotic_high, rankbased_level2bs_high)
# create_table_for_tightness_measure(
#   summary=tabb1,
#   metric_type="$T_3$",
#   equicorr)
```


```{r include = FALSE}
# tabb <- preprocess_tightness_measure(combined, "t1", equicorr, FALSE)
# 
# if (!equicorr) {
#   tabb <- tabb %>% select(-c(r, blocks))
# }

# create_table_for_tightness_measure(
#   summary=tabb,
#   metric_type="T1", equicorr, FALSE)
```

```{r include = FALSE}
# tabb <- preprocess_tightness_measure(combined, "t2", equicorr, FALSE)
# 
# if (!equicorr) {
#   tabb <- tabb %>% select(-c(r, blocks))
# }


# create_table_for_tightness_measure(
#   summary=tabb, 
#   metric_type="T2", equicorr, FALSE)
```

```{r include = FALSE}
# tabb <- preprocess_tightness_measure(combined, "t3", equicorr, FALSE)
# 
# if (!equicorr) {
#   tabb <- tabb %>% select(-c(r, blocks))
# }

# create_table_for_tightness_measure(
#   summary=tabb, 
#   metric_type="T3", equicorr, FALSE)
```


\elandscape


```{r simulation-table1, results='asis', include=FALSE}
library(dplyr)
library(tidyr)
mean <- 23.8
sds <-c('low', 'medium', 'high')# c(2, 3.6, 6)
Ks <- c(10, 20, 30, 40, 50)
#corrs <- c(0.1,0.5,0.9)
alphas <- c(0.05)#c(0.05, 0.1, 0.15, 0.2)

theta <- c()
std <- c()
K <- c()
i <-1   # initialize index

for (k in Ks) {
  for (sd in sds) {

    set.seed(123974)
    true_theta <- sd #rnorm(k, mean, sd)
    value_to_add <- true_theta#paste(round(true_theta,1), collapse = ", ")
    theta[i] <- value_to_add
    std[i] <- sd
    K[i] <- k
    i <- i + 1
  }
}

reals <- data.frame(theta, K, std)


# grid <- grid %>%

# grid#dplyr::inner_join(grid, reals, by = c("std", "K"))

reals <- data.frame(theta, K, std)

K <- c(10, 20, 30, 40, 50)
sd <-c(2.0, 3.6, 6.0)# my_list
R_type <- c("R_eq", "R_block")

reals$R <- rep(list(R_type), nrow(reals))
table_to_plot <- reals %>%
  unnest(R) %>%
  mutate(
    `$\\mathbf{R}$` = case_when(
      R == "R_eq" ~ "$\\mathbf{R}_{\\text{eq}}, \\rho = 0.1, 0.5, 0.9$",
      R == "R_block" ~ "$\\mathbf{R}_{\\text{block}} \\text{(2 or 3 blocks)}$"
    )
  ) %>%
  select(theta, `$\\mathbf{R}$`, K)
```

```{r asis = TRUE, include = FALSE}
library(kableExtra)


kable(table_to_plot, "latex", booktabs = TRUE, escape = FALSE,linesep = "",
      longtable = TRUE) %>%
  column_spec(1, width = "10cm") %>%    # wrap column 1
  column_spec(2, width = "5cm") %>%
  kable_styling(
    latex_options = c("striped", "repeat_header", "HOLD_position"),
    stripe_color = "gray!15"  # light gray, can change
  )
```

## Codes for algorithm 1 {.unnumbered}

```{r simulation-table, results='asis', include=FALSE}
library(dplyr)
library(tidyr)
mean <- 23.8
sds <- c(2, 3.6, 6)
Ks <- c(10, 20, 30, 40, 50)
#corrs <- c(0.1,0.5,0.9)
alphas <- c(0.05)#c(0.05, 0.1, 0.15, 0.2)

theta <- c()
std <- c()
K <- c()
i <- 1   # initialize index

for (k in Ks) {
  for (sd in sds) {

    set.seed(123974)
    true_theta <- rnorm(k, mean, sd)
    value_to_add <- paste(round(true_theta,1), collapse = ", ")
    theta[i] <- value_to_add
    std[i] <- sd
    K[i] <- k
    i <- i + 1
  }
}

reals <- data.frame(theta, K, std)


# grid <- grid %>%

# grid#dplyr::inner_join(grid, reals, by = c("std", "K"))

reals <- data.frame(theta, K, std)

K <- c(10, 20, 30, 40, 50)
sd <-c(2.0, 3.6, 6.0)# my_list
R_type <- c("R_eq", "R_block")

reals$R <- rep(list(R_type), nrow(reals))
table_to_plot <- reals %>%
  unnest(R) %>%
  mutate(
    `$\\mathbf{R}$` = case_when(
      R == "R_eq" ~ "$\\mathbf{R}_{\\text{eq}}, \\rho = 0.1, 0.5, 0.9$",
      R == "R_block" ~ "$\\mathbf{R}_{\\text{block}} \\text{(2 or 3 blocks)}$"
    )
  ) %>%
  select(theta, `$\\mathbf{R}$`)
```

```{r asis = TRUE, include = FALSE}
library(kableExtra)


kable(table_to_plot, "latex", booktabs = TRUE, escape = FALSE,linesep = "",
      longtable = TRUE) %>%
  column_spec(1, width = "10cm") %>%    # wrap column 1
  column_spec(2, width = "5cm") %>%
  kable_styling(
    latex_options = c("striped", "repeat_header", "HOLD_position"),
    stripe_color = "gray!15"  # light gray, can change
  )
```

```{r, results='asis', echo=FALSE, warning=FALSE, include=FALSE}
code <- readLines("../../R/simulate/compute_ci.R")
cat("```r\n", paste(code, collapse = "\n"), "\n```")
```

## Codes for algorithm 2 {.unnumbered}

```{r, results='asis', echo=FALSE, warning=FALSE, include=FALSE}
code <- readLines("../../R/simulate/compute_metrics.R")
cat("```r\n", paste(code, collapse = "\n"), "\n```")
```

## Codes for simulation {.unnumbered}

```{r, results='asis', echo=FALSE, warning=FALSE, include=FALSE}
code <- readLines("../../R/simulate/implement.R")
cat("```r\n", paste(code, collapse = "\n"), "\n```")
```

